---
title: "Process_landcover"
format: html
editor: visual
---

```{r}
knitr::opts_chunk$set(echo=F, message=F, warning=F)

# Load libraries
library(tidyverse)
library(sf)
library(terra)
library(units)
library(raster)
library(rgeos)
library(tmap)
library(RColorBrewer)
```

# Land cover classes

Reclassify land cover and save as new tiff file.

```{r}
watershed70 <- read_sf("Raw_Data/Shape_files/catchment_delineation/RefElv.shp") 

# Land cover raster files from 2018
LandCoverRast2018 <- rast("Raw_Data/land_cover/Raster/u2018_clc2018_v2020_20u1_raster100m/DATA/U2018_CLC2018_V2020_20u1.tif")

# Crop the raster files (which cover all of Europe) to the pasvik watershed outline
watershed70 = st_transform(watershed70, "EPSG:3035")

LandCoverRast2018_2 <- crop(LandCoverRast2018, vect(watershed70))
LandCoverRast2018_crop <- mask(LandCoverRast2018_2, vect(watershed70))
LandCoverRast2018_proj <- terra::aggregate(LandCoverRast2018_crop, fact = 2)

levels(LandCoverRast2018_crop)
freq(LandCoverRast2018_crop)

m <- c(1, 45,
       2, 45,
       3, 45,
       4, 45,
       5, 45,
       6, 45,
       7, 45,
       8, 45,
       9, 45,
       10, 45,
       11, 45,
       12, 45,
       13, 45,
       14, 45,
       15, 45,
       16, 45,
       17, 45,
       18, 45,
       19, 45,
       20, 45,
       22, 45,
       26, 45,
       28, 45,
       30, 45,
       33, 45,
       35, 45,
       37, 45,
       38, 45,
       39, 45,
       40, 45,
       42, 45,
       43, 45)

#Reclassify the map with help of the matrix
rclmat <- matrix(m, ncol=2, byrow=TRUE) # important to specify number of columns = 2, (e.g. could put 3 if three columns). 
veg_rcl <- classify(LandCoverRast2018_proj, rclmat) # This can take hours! 

writeRaster(veg_rcl, "Raw_Data/land_cover/land_cover_reclass.tif")
saveRDS(veg_rcl, "Raw_Data/land_cover/land_cover_reclass.RData")
```


# Calcualte and export land cover (% of each category) for each catchment individually. 
```{r}
# Load key files
watershed70 <- read_sf("Raw_Data/Shape_files/catchment_delineation/RefElv.shp") 
watershed70 = st_transform(watershed70, "EPSG:3035")

# Land cover raster files from 2018
LandCoverRast2018 <- rast("Raw_Data/land_cover/Raster/u2018_clc2018_v2020_20u1_raster100m/DATA/U2018_CLC2018_V2020_20u1.tif")

m <- c(1, 45,
       2, 45,
       3, 45,
       4, 45,
       5, 45,
       6, 45,
       7, 45,
       8, 45,
       9, 45,
       10, 45,
       11, 45,
       12, 45,
       13, 45,
       14, 45,
       15, 45,
       16, 45,
       17, 45,
       18, 45,
       19, 45,
       20, 45,
       22, 45,
       26, 45,
       28, 45,
       30, 45,
       33, 45,
       35, 45,
       37, 45,
       38, 45,
       39, 45,
       40, 45,
       42, 45,
       43, 45)

#Reclassify the map with help of the matrix
rclmat <- matrix(m, ncol=2, byrow=TRUE)

# Function for cropping landcover file to each watershed one at a time. reclassify and extract. 
landcover_extract = function(x){
  # Crop the raster to the size of the watershed
  LandCoverRast2018_2 <- crop(LandCoverRast2018, vect(x))
  LandCoverRast2018_crop <- mask(LandCoverRast2018_2, vect(x))
  
  # Reclassify to new categories and extract data. 
  veg_rcl <- classify(LandCoverRast2018_crop, rclmat) 
  veg_crop <- crop(veg_rcl, vect(x))
  veg_crop <- mask(veg_crop, vect(x))
  landcover_df <- terra::extract(veg_crop, vect(x)) 
  
  # Summarize the data
  landcover_df$count <- 1 # add coumn to aid summarization
  watershed_class_proportion <- landcover_df %>%
    dplyr::select(LABEL3, count) %>%
    group_by(LABEL3) %>% 
    summarise_at(c("count"), sum, na.rm = TRUE) %>% 
    pivot_wider(names_from = LABEL3, values_from = 'count')
  
  # Calculate the percentages per vegetation class and watershed
  watershed_class_proportion <- watershed_class_proportion %>% 
    mutate(total = sum(c_across(where(is.numeric)), na.rm = TRUE)) %>% 
    ungroup() %>% 
    mutate(across(where(is.numeric), ~ . / total*100))
  
  return(watershed_class_proportion)
}

y <- watershed70 %>%
  nest_by(site_id) %>% 
  mutate(landcover_df = list(landcover_extract(data)))

landcover_df <- y %>% 
  dplyr::select(c(site_id, landcover_df)) %>% unnest(landcover_df) %>% 
  dplyr::select(-c(total)) %>% 
  rename("Agriculture" = "21",
         "Broad-leaved forest"= "23",
         "Coniferous forest" = "24",
         "Mixed forest" = "25",
         "Moors and heathland" = "27",
         "woodland-scrub" = "29",
         "Bare rocks" = "31",
         "Sparse vegetation"= "32",
         "Glacier" = "34",
         "Peat bogs" = "36", 
         "Water bodies" =  "41",
         "Other" = "45") 

landcover_df[is.na(landcover_df)] = 0
write_csv(landcover_df, file = "Clean_Data/Intermediate/landcover_df.csv")
```






# Wetness Index

Load files, crop to watershed and save tiff file.
```{r}
# Load the wetness raster files from the wetness folder, crop to watershed and save as a tif file. This only needs to be run once! 
watershed70 <- read_sf("Raw_Data/Shape_files/catchment_delineation/RefElv.shp") 
watershed70 = st_transform(watershed70, "EPSG:3035")

readandproject = function(x){
  lapply(x, function(x){
    r = rast(x)
    crs(r) = "EPSG:3035"
    r_crop <- crop(r, vect(watershed70))
    r_crop2 <- mask(r_crop, vect(watershed70))
    r_proj <- terra::aggregate(r_crop2, fact = 2)
    return(r_proj)
  }
  )
}

list_of_files <- list.files(path = "Raw_Data/land_cover/wetness/WAW_2018_010m_no_03035_v020/DATA/Yes/",
                            pattern='\\.tif$', full.names=TRUE)

y <- purrr::map(list_of_files, readandproject) 

rsrc <- sprc(unlist(y))
m <- mosaic(rsrc)

wetness_proj <- terra::aggregate(m, fact = 2)
writeRaster(wetness_proj, "Raw_Data/land_cover/wetness/wetness_all.tif")
#saveRDS(m, "Raw_Data/land_cover/wetness/wetness_all.RData")
```



# Calcualte and export wetness index (% of each category) for each catchment individually. (((IN PREP)))
```{r}
# Load key files
watershed70 <- read_sf("Raw_Data/Shape_files/catchment_delineation/RefElv.shp") 
watershed70 = st_transform(watershed70, "EPSG:3035")

# Land cover raster files from 2018
wetness <- rast("Raw_Data/land_cover/wetness/wetness_all.tif")


# Function for cropping wetness file to each watershed one at a time and extracting and summaring the results. 

landcover_extract = function(x){
 
   # Crop the raster to the size of the watershed
    wetness_2 <- crop(wetness, vect(watershed2))
    wetness_crop <- mask(wetness_2, vect(watershed2))
    wetness_df <- terra::extract(wetness_crop, vect(watershed2)) 
  
  # Summarize the data
  wetness_df$count <- 1 # add column to aid summarization
  watershed_class_proportion <- wetness_df %>%
    dplyr::select(AREA_KM2, ID) %>%
    group_by(ID) %>% 
    summarise_at(c("AREA_KM2"), sum, na.rm = TRUE) %>% 
    pivot_wider(names_from = AREA_KM2, values_from = 'ID')
  
  # Calculate the percentages per vegetation class and watershed
  watershed_class_proportion <- watershed_class_proportion %>% 
    mutate(total = sum(c_across(where(is.numeric)), na.rm = TRUE)) %>% 
    ungroup() %>% 
    mutate(across(where(is.numeric), ~ . / total*100))
  
  return(watershed_class_proportion)
}


watershed2 <- watershed70 %>% 
  filter(site_id %in% c("O_002-305_Atn_DAN11"))


y <- watershed70 %>%
  nest_by(site_id) %>% 
  mutate(landcover_df = list(landcover_extract(data)))

wetness_2 <- crop(wetness, vect(watershed70))
wetness_crop <- mask(wetness_2, vect(watershed70))
wetness_df <- terra::extract(wetness_crop, vect(watershed70)) 

write_csv(wetness_df, file = "Clean_Data/Intermediate/wetness_df.csv")
```




# Buffer Zone: extract land cover from buffer. ####Not working yet--too many rivers?
```{r}
rivers <- read_sf("Raw_Data/Shape_files/NVE_RefElv/Combined_Output/Hovedelv_all.shp")
riverline_projected = st_transform(rivers, "EPSG:3035")
riverline_shed <- st_intersection(riverline_projected, watershed70)
  
# Make a buffer at 50m distance
buffer50 <- st_buffer(riverline_shed, dist = 50) # buffer of 50 meters around the lines
v50 <- vect(buffer50) # vectorize the buffer

##Now we turn the buffer into a raster layer
r50 <- rast(v50,res=10) # empty raster with the extent of the buffer shapefile and resolution of 10m 
z50 <- rasterize(v50, r50) # rasterize the buffer
names(z50)[1] <- "buff50" # Give the buffer a unique name
```
# Buffer
```{r}
# Load key files
#watershed2 <- watershed70 %>% 
  #filter(site_id %in% c("O_002-305_Atn_DAN11"))


watershed70 <- read_sf("Raw_Data/Shape_files/catchment_delineation/RefElv.shp") 
watershed70 = st_transform(watershed70, "EPSG:3035")

rivers <- read_sf("Raw_Data/Shape_files/NVE_RefElv/Combined_Output/Hovedelv_all.shp")
riverline_projected = st_transform(rivers, "EPSG:3035")
  
# Land cover raster files from 2018
LandCoverRast2018 <- rast("Raw_Data/land_cover/Raster/u2018_clc2018_v2020_20u1_raster100m/DATA/U2018_CLC2018_V2020_20u1.tif")

m <- c(1, 45,
       2, 45,
       3, 45,
       4, 45,
       5, 45,
       6, 45,
       7, 45,
       8, 45,
       9, 45,
       10, 45,
       11, 45,
       12, 45,
       13, 45,
       14, 45,
       15, 45,
       16, 45,
       17, 45,
       18, 45,
       19, 45,
       20, 45,
       22, 45,
       26, 45,
       28, 45,
       30, 45,
       33, 45,
       35, 45,
       37, 45,
       38, 45,
       39, 45,
       40, 45,
       42, 45,
       43, 45)

#Reclassify the map with help of the matrix
rclmat <- matrix(m, ncol=2, byrow=TRUE)

# Function for cropping landcover file to each watershed one at a time. reclassify and extract. 
landcover_extract = function(x){
  
  # Make a buffer at 50m distance
  riverline_shed <- st_intersection(riverline_projected, x)
  buffer50 <- st_buffer(riverline_shed, dist = 50) # buffer of 50 meters around the lines
  v50 <- vect(buffer50) # vectorize the buffer

  # Now we turn the buffer into a raster layer
  r50 <- rast(v50,res=10) # empty raster with the extent of the buffer shapefile and resolution of 10m 
  z50 <- rasterize(v50, r50) # rasterize the buffer
  names(z50)[1] <- "buff50" # Give the buffer a unique name

  # Crop the raster to the size of the watershed
  LandCoverRast2018_2 <- crop(LandCoverRast2018, vect(x))
  LandCoverRast2018_crop <- mask(LandCoverRast2018_2, vect(x))
  z50_2 <- crop(z50, vect(x))
  z50_crop <- mask(z50_2, vect(x))
  # Reclassify to new categories and extract data. 
  veg_rcl <- classify(LandCoverRast2018_crop, rclmat) 
  veg_crop <- crop(veg_rcl, vect(x))
  veg_crop <- mask(veg_crop, vect(x))
  buffer50_prj <- project(z50_crop, veg_crop) # project buffer to match 

  #We stack all the layers on top of each other
  stack <- c(veg_crop, buffer50_prj)

  #We extract all the stacked data
  landcover_buffer_df <- terra::extract(stack, vect(x)) 
  landcover_buffer_df <- landcover_buffer_df %>% 
    mutate(river_buffer50 = ifelse(grepl ("elva", buff50), "1", buff50))

  # Summarize the data
  landcover_buffer_df$count <- 1 # add column to aid summarization
  watershed_class_proportion <- landcover_buffer_df %>%
    filter(river_buffer50 == "1") %>% 
    dplyr::select(LABEL3, count) %>%
    group_by(LABEL3) %>% 
    summarise_at(c("count"), sum, na.rm = TRUE) %>% 
    pivot_wider(names_from = LABEL3, values_from = 'count')
  
  # Calculate the percentages per vegetation class and watershed
  watershed_class_proportion <- watershed_class_proportion %>% 
    mutate(total = sum(c_across(where(is.numeric)), na.rm = TRUE)) %>% 
    ungroup() %>% 
    mutate(across(where(is.numeric), ~ . / total*100))
  
  return(watershed_class_proportion)
}

y <- watershed70 %>%
  filter(!site_id %in% c("F_221-93_Kob", "F_238-48_San", "M_123-499_Hom", "M_128-169_Nod")) %>% 
  nest_by(site_id) %>% 
  mutate(landcover_buffer_df = list(landcover_extract(data)))

landcover_buffer_df <- y %>% 
  dplyr::select(c(site_id, landcover_buffer_df)) %>% unnest(landcover_buffer_df) %>% 
  dplyr::select(-c(total)) %>% 
  rename("Agriculture" = "21",
         "Broad-leaved forest"= "23",
         "Coniferous forest" = "24",
         "Mixed forest" = "25",
         "Moors and heathland" = "27",
         "woodland-scrub" = "29",
         "Bare rocks" = "31",
         "Sparse vegetation"= "32",
         "Glacier" = "34",
         "Peat bogs" = "36", 
         "Water bodies" =  "41",
         "Other" = "45") 

landcover_buffer_df[is.na(landcover_buffer_df)] = 0
write_csv(landcover_df, file = "Clean_Data/Intermediate/landcover_buffer_df.csv")
```





# Load Riparian zone land cover files

```{r}
# Load vector data
watershed70 <- read_sf("Raw_Data/Shape_files/catchment_delineation/RefElv.shp") 

r = st_read("Raw_Data/land_cover/Riparian/rpz_DU027A.shp", driver = 'ESRI Shapefile', stringsAsFactors =F) 
r_proj = st_transform(r, "EPSG:25833") # Update to watershed coordinate systems
r_shed <- st_intersection(r_proj, watershed70) # Clip to watershed extent

r2 = read_sf("Raw_Data/land_cover/Riparian/rpz_DU028A.shp", driver = 'ESRI Shapefile') 
r_proj2 = st_transform(r2, "EPSG:25833") # Update to watershed coordinate systems
r_shed2 <- st_intersection(r_proj2, watershed70) # Clip to watershed extent

r3 = read_sf("Raw_Data/land_cover/Riparian/rpz_DU030A.shp", driver = 'ESRI Shapefile') 
r_proj3 = st_transform(r3, "EPSG:25833") # Update to watershed coordinate systems
r_shed3 <- st_intersection(r_proj3, watershed70) # Clip to watershed extent

r4 = read_sf("Raw_Data/land_cover/Riparian/rpz_DU037A.shp", driver = 'ESRI Shapefile') 
r_proj4 = st_transform(r4, "EPSG:25833") # Update to watershed coordinate systems
r_shed4 <- st_intersection(r_proj4, watershed70) # Clip to watershed extent

c <- bind_rows(r_shed, r_shed2, r_shed3, r_shed4) # Combine to one shape file
st_write(c, "Raw_Data/Raw_Data/land_cover/Riparian.shp", driver="ESRI Shapefile")
```

```{r}
watershed2 <- watershed70 %>% 
  filter(site_id %in% c("O_002-305_Atn_DAN11"))

riparian_zone <- read_sf("Raw_Data/Raw_Data/land_cover/Riparian.shp") # Load combined file. 

v50 <- vect(riparian_zone) # Vectorize the shape file
r50 <- rast(v50,res=10) #make a raster the size of the shape fil with a resolution of 10. 

z50 <- rasterize(watershed2, r50, "name") #rasterize to the size of the watershed. 
names(z50)[1] <- "riparian"

z50_2 <- crop(z50, vect(watershed2))
z50_crop <- mask(z50_2, vect(watershed2))

landcover_buffer_df <- terra::extract(z50_crop, vect(watershed2)) 


# Summarize the data
landcover_buffer_df$count <- 1 # add column to aid summarization

watershed_class_proportion <- landcover_buffer_df %>%
    dplyr::select(LABEL3, count) %>%
    group_by(LABEL3) %>% 
    summarise_at(c("count"), sum, na.rm = TRUE) %>% 
    pivot_wider(names_from = LABEL3, values_from = 'count')
  
  # Calculate the percentages per vegetation class and watershed
watershed_class_proportion <- watershed_class_proportion %>% 
    mutate(total = sum(c_across(where(is.numeric)), na.rm = TRUE)) %>% 
    ungroup() %>% 
    mutate(across(where(is.numeric), ~ . / total*100))
  
  return(watershed_class_proportion)
  
```

