---
title: "RefElv_WaterChem"
format: html
---

```{r}
library(tidyverse)
library(mgcv)
library(lubridate)
library(jpeg)
library(pdftools)

Water_Chem_select <- read_csv("Clean_Data/Water_Chem_select.csv")
Station_Info <- read_csv("Clean_Data/Station_Info.csv")
```

```{r}
# Summary table of water chem

Sum_table2 <- Water_Chem_select %>% 
  mutate(year = year(Date)) %>% 
  dplyr::select(c(site_id, year, okoregion, group, Temp_C, Ca_mg_L, pH, ANC_µEkv_L, SO4_mg_L, Fe_ug_L, DOC_mg_L, Water_Color_mgPt_l, TotP_ug_L, TotN_ug_L, NO3_ug_L, TN_TP, DIN_TP)) %>% 
  pivot_longer(cols = -c(site_id, year, okoregion, group), names_to = "variable", values_to = "value") %>% 
  drop_na(value) %>% mutate(value = as.numeric(value) %>% round(2)) %>% 
  drop_na(group) %>% 
  filter(!group %in% c("incomplete", "'18/'19/'20/'21")) %>% 
  group_by(site_id, year, variable) %>% 
  summarise(n = n(), median_value1 = median(value), okoregion = okoregion) %>% 
  ungroup() %>% distinct() %>% 
  group_by(okoregion, variable) %>% 
  summarise(n = n(), median_median = (median(median_value1)%>% round(1)),
            sd_median = (sd(median_value1) %>% round(1))) %>% 
  distinct() %>% 
  mutate(stat = glue("{median_median} [{sd_median}]")) %>% 
  mutate(n = glue("{n}")) %>% 
  dplyr::select(okoregion, variable, stat) %>% 
  pivot_wider(names_from = "okoregion", values_from = "stat")


### Station Information

Sum_table3 <- Station_Info %>% 
  dplyr::select(c(site_id, okoregion, group, area_km2, mean_elevation, mean_slope, mean_annual_tm, sum_annual_rr, mean_annual_gwb_q, mean_annual_gwb_sssrel)) %>% 
  mutate(sum_annual_rr_m = sum_annual_rr/1000) %>% 
  dplyr::select(-c(sum_annual_rr)) %>% 
  pivot_longer(cols = -c(site_id, okoregion, group), names_to = "variable", values_to = "value") %>% drop_na(value) %>% 
  filter(!group %in% c("incomplete", "'18/'19/'20/'21")) %>% 
  ungroup() %>% distinct() %>% 
  group_by(okoregion, variable) %>%  
  summarise(n = n(), median_value = (median(value)%>% round(1)),
            sd_median = (sd(value) %>% round(1))) %>% 
  distinct() %>% 
  mutate(stat = glue("{median_value} [{sd_median}]")) %>% 
  mutate(n = glue("{n}")) %>% 
  dplyr::select(okoregion, variable, n, stat) %>%
  pivot_wider(names_from = "variable", values_from = "stat") %>% 
  pivot_longer(cols = -c(okoregion), names_to = "variable", values_to = "stat") %>% drop_na() %>% 
  pivot_wider(names_from = "okoregion", values_from = "stat")

Sum_table <- full_join(Sum_table3, Sum_table2)
write_csv(Sum_table, "clean_Data/Sum_table.csv")
```

```{r}
XX<- read_csv("Clean_Data/Water_Chem_Climate.csv") %>% 
  dplyr::select(c(Na_mg_L, site_id, rapportnavn, Date)) %>% distinct() %>% 
  arrange(site_id)

X <- XX %>% dplyr::select(site_id) %>% distinct()

Plot1 <- XX %>% 
  mutate(year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(!year %in% c("2017", "2022")) %>% 
  ggplot() +
  geom_point(aes(x = Date, y = Na_mg_L, color = factor(year))) +
  scale_y_log10() + 
  facet_wrap(~site_id, ncol = 3)

ggsave("Figures/Na.pdf", Plot1, width = 7, height = 25, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Na.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Na.jpeg")
```


```{r}

Plot_overview <- Water_Chem_select %>% 
  dplyr::select(c(site_id, okoregion, group, Temp_C, Ca_mg_L, pH, ANC_µEkv_L, SO4_mg_L, Fe_ug_L, DOC_mg_L, Water_Color_mgPt_l, TotP_ug_L, TotN_ug_L, NO3_ug_L, TN_TP, DIN_TP)) %>% 
  pivot_longer(cols = -c(site_id, okoregion, group), names_to = "variable", values_to = "value") %>%
  drop_na(value) %>% mutate(value = as.numeric(value) %>% round(2)) %>% 
  drop_na(group) %>% 
  filter(!group %in% c("incomplete", "'18/'19/'20/'21")) %>% 
  ggplot() + 
  geom_boxplot(aes(x = okoregion, y =value, color = group)) +
  facet_wrap(~variable, scales = "free")


#Phys
Phys <- Water_Chem_select %>% 
  dplyr::select(c(site_id, Date, okoregion, Temp_C, Ca_mg_L, pH, ANC_µEkv_L, SO4_mg_L, Fe_ug_L, DOC_mg_L, Water_Color_mgPt_l, TotP_ug_L, TotN_ug_L, NO3_ug_L, TN_TP, DIN_TP)) %>% 
  pivot_longer(cols= -c(site_id, Date, okoregion), names_to = "Variable", values_to = "Measurement") %>% 
  mutate(Measurement = as.numeric(Measurement) %>% round(2)) %>% 
  mutate(year = year(Date)) %>% 
  drop_na(Measurement) %>% drop_na(okoregion)

Phys$Variable <- factor(Phys$Variable,
                        levels = c("Temp_C", "Turbidity", "Conductivity_mS_m", "pH", 
                 "Water_Color_mgPt_l", "Alkalinity_mmol_L", "ANC_µEkv_L"),
                        labels = c(bquote('Temp'~ (C)),
                                   bquote('Turbidity'~ (NTU)),
                                   bquote('Conductivity'~ (mS~m^-1)),
                                   bquote('pH'),
                                   bquote('Water Color'~ (mgPt~L^-1)),
                                   bquote('Alkalinity'~ (mmol~L^-1)),             
                                   bquote('ANC'~ (µEkv~L^-1))))

Plot1 <- Phys %>% 
  ggplot(aes(x = year, y = Measurement, fill = factor(year))) + 
  geom_boxplot() +
  scale_y_log10 () + 
  facet_grid(Variable~okoregion, scales = "free") +
  theme_bw() +
  xlab(NULL) 

ggsave("Figures/Raw_boxplot.pdf", Plot1, width = 12, height = 8, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Raw_boxplot.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Raw_boxplot.jpeg")
```

# Raw Plots of Water Chemistry by rivers

```{r}

#Phys
Phys <- Water_Chem_Climate %>% 
  dplyr::select(c(site_id, Date, mean_elevation, Temp_C, Turbidity, Conductivity_mS_m, pH, Water_Color_mgPt_l, Alkalinity_mmol_L, ANC_µEkv_L)) %>% 
  pivot_longer(cols= -c(site_id, Date, mean_elevation), names_to = "Variable", values_to = "Measurement") %>% 
  mutate(Elevation = ifelse(mean_elevation < 900, "low", "high")) %>% 
  drop_na(Elevation)


Phys$Variable <- factor(Phys$Variable,
                        levels = c("Temp_C", "Turbidity", "Conductivity_mS_m", "pH", 
                 "Water_Color_mgPt_l", "Alkalinity_mmol_L", "ANC_µEkv_L"),
                        labels = c(bquote('Temp'~ (C)),
                                   bquote('Turbidity'~ (NTU)),
                                   bquote('Conductivity'~ (mS~m^-1)),
                                   bquote('pH'),
                                   bquote('Water Color'~ (mgPt~L^-1)),
                                   bquote('Alkalinity'~ (mmol~L^-1)),             
                                   bquote('ANC'~ (µEkv~L^-1))))

Plot1 <- Phys %>% 
  ggplot(aes(x = Date, y = Measurement)) + 
  geom_point(size = 0.5, color ="gray70", alpha = 0.4) +
  scale_y_log10 () + 
  geom_smooth(aes(color = site_id), method = "gam", se = FALSE) +
  facet_wrap(~ Variable, scales = "free", labeller = label_parsed) +
  theme_bw() +
  xlab(NULL) 

ggsave("Figures/Phys_sites.pdf", Plot1, width = 9, height = 5.5, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Phys_sites.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Phys_sites.jpeg")

#Metals
Metals <- Water_Chem_Climate %>% 
  dplyr::select(c(site_id, Date, mean_elevation, Fe_ug_L, Cd_ug_L, Cu_ug_L, Cr_ug_L, Pb_ug_L, Ni_ug_L, Zn_ug_L)) %>% 
  pivot_longer(cols= -c(site_id, Date, mean_elevation), names_to = "Variable", values_to = "Measurement")  %>%
  mutate(Elevation = ifelse(mean_elevation < 900, "low", "high")) %>% 
  drop_na(Elevation)

Metals$Variable <- factor(Metals$Variable,
                        levels = c("Fe_ug_L", "Cd_ug_L", "Cr_ug_L", "Cu_ug_L",
                                   "Pb_ug_L", "Ni_ug_L", "Zn_ug_L"),
                        labels = c(bquote('Fe'~ (μg~L^-1)),
                                   bquote('Cd'~ (μg~L^-1)),
                                   bquote('Cr'~ (μg~L^-1)),
                                   bquote('Cu'~ (μg~L^-1)),
                                   bquote('Pb'~ (μg~L^-1)),
                                   bquote('Ni'~ (μg~L^-1)),             
                                   bquote('Zn'~ (μg~L^-1))))

Plot2 <- Metals %>%  
  ggplot(aes(x = Date, y = Measurement)) + 
  geom_point(size = 0.5, color ="gray70", alpha = 0.4) +
  scale_y_log10 () + 
  geom_smooth(aes(color = site_id), method = "gam", se = FALSE) +
  facet_wrap(~ Variable, scales = "free", labeller = label_parsed) +
  theme_bw() +
  xlab(NULL) 

ggsave("Figures/Metals_sites.pdf", Plot2, width = 9, height = 5.5, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Metals_sites.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Metals_sites.jpeg")


#Metals
Metals2 <- Water_Chem_Climate %>% 
  dplyr::select(c(site_id, Date, mean_elevation, Al_ug_L, Al_il_ug_L, Al_l_ug_L, Al_r_ug_L)) %>% 
  pivot_longer(cols= -c(site_id, Date, mean_elevation), names_to = "Variable", values_to = "Measurement") %>% 
  mutate(Elevation = ifelse(mean_elevation < 900, "low", "high")) %>% 
  drop_na(Elevation)

Metals2$Variable <- factor(Metals2$Variable,
                        levels = c("Al_ug_L", "Al_il_ug_L", "Al_l_ug_L", "Al_r_ug_L"),
                        labels = c(bquote('Al'~ (μg~L^-1)),
                                   bquote('Al- ikke labil'~ (μg~L^-1)),
                                   bquote('Al - labil'~ (μg~L^-1)),
                                   bquote('Al - reactive'~ (μg~L^-1))))

Plot3 <- Metals2 %>% 
  ggplot(aes(x = Date, y = Measurement)) + 
  geom_point(size = 0.5, color ="gray70", alpha = 0.4) +
  scale_y_log10 () + 
  geom_smooth(aes(color = site_id), method = "gam", se = FALSE) +
  facet_wrap(~ Variable, scales = "free", labeller = label_parsed) +
  theme_bw() +
  xlab(NULL) 

ggsave("Figures/Metals2_sites.pdf", Plot3, width = 7, height = 5, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Metals2_sites.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Metals2_sites.jpeg")


#Ions
Ions <- Water_Chem_Climate %>% 
  dplyr::select(c(site_id, Date, mean_elevation, Mg_mg_L, K_mg_L, Ca_mg_L, SO4_mg_L, Na_mg_L)) %>% 
  pivot_longer(cols= -c(site_id, Date, mean_elevation), names_to = "Variable", values_to = "Measurement") %>% 
  mutate(Elevation = ifelse(mean_elevation < 900, "low", "high")) %>% 
  drop_na(Elevation)

Ions$Variable <- factor(Ions$Variable,
                        levels = c("Mg_mg_L", "K_mg_L", "Ca_mg_L", "SO4_mg_L", "Na_mg_L"),
                        labels = c(bquote('Mg'~ (mg~L^-1)),
                                   bquote('K'~ (mg~L^-1)),
                                   bquote('Ca'~ (mg~L^-1)),
                                   bquote('SO'[4]~ (mg~L^-1)),
                                   bquote('Na'~ (mg~L^-1))))

Plot4 <- Ions %>% ggplot(aes(x = Date, y = Measurement)) + 
  geom_point(size = 0.5, color ="gray70", alpha = 0.4) +
  scale_y_log10 () + 
  geom_smooth(aes(color = site_id), method = "gam", se = FALSE) +
  facet_wrap(~ Variable, scales = "free", labeller = label_parsed) +
  theme_bw() +
  xlab(NULL) 

ggsave("Figures/Ions_sites.pdf", Plot4, width = 8, height = 3.75, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Ions_sites.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Ions_sites.jpeg")


#Nutrients

Nutrients <- Water_Chem_Climate %>% 
  dplyr::select(c(site_id, Date, mean_elevation, TotP_ug_L, TotN_ug_L, PO4_ug_L, NO3_ug_L, SiO2_mg_L)) %>% 
  pivot_longer(cols= -c(site_id, Date, mean_elevation), names_to = "Variable", values_to = "Measurement") %>% 
  mutate(Elevation = ifelse(mean_elevation < 900, "low", "high")) %>% 
  drop_na(Elevation)

Nutrients$Variable <- factor(Nutrients$Variable,
                        levels = c("TotP_ug_L", "TotN_ug_L", "PO4_ug_L", "NO3_ug_L", "SiO2_mg_L"),
                        labels = c(bquote('TotP'~ (μg~L^-1)),
                                   bquote('TotN'~ (μg~L^-1)),
                                   bquote('PO'[4]~ (μg~L^-1)),
                                   bquote('NO'[3]~ (μg~L^-1)),
                                   bquote('SiO'[2]~ (mg~L^-1))))
  
Plot5 <- Nutrients %>% 
  ggplot(aes(x = Date, y = Measurement)) + 
  geom_point(size = 0.5, color ="gray70", alpha = 0.4) +
  scale_y_log10 () + 
  geom_smooth(aes(color = site_id), method = "gam", se = FALSE) +
  facet_wrap(~ Variable, scales = "free", labeller = label_parsed) +
  theme_bw() +
  xlab(NULL) 

ggsave("Figures/Nutrients_sites.pdf", Plot5, width = 9, height = 5, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Nutrients_sites.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Nutrients_sites.jpeg")


#Carbon
Carbon <- Water_Chem_Climate %>% 
  dplyr::select(c(site_id, Date, mean_elevation, DOC_mg_L, TOC_mg_L)) %>% 
  pivot_longer(cols= -c(site_id, Date, mean_elevation), names_to = "Variable", values_to = "Measurement") %>% 
  mutate(Elevation = ifelse(mean_elevation < 900, "low", "high")) %>% 
  drop_na(Elevation)
  
Carbon$Variable <- factor(Carbon$Variable, levels = c("DOC_mg_L", "TOC_mg_L"),
                          labels = c(bquote('DOC'~ (mg~L^-1)), 
                                     bquote('TOC'~ (mg~L^-1))))

Plot6 <- Carbon %>% 
  ggplot(aes(x = Date, y = Measurement)) + 
  geom_point(size = 0.5, color ="gray70", alpha = 0.4) +
  scale_y_log10 () + 
  geom_smooth(aes(color = site_id), method = "gam", se = FALSE) +
  facet_wrap(~ Variable, scales = "free", labeller = label_parsed) +
  theme_bw() +
  xlab(NULL) 

ggsave("Figures/Carbon_sites.pdf", Plot6, width = 6, height = 2, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Carbon_sites.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Carbon_sites.jpeg")
```




# Water Chemistry by groups color = Ecoregion

## Physical

```{r}
Water_Chem_Climate <- read_csv("Clean_Data/Water_Chem_Climate.csv")

# Phys: 2018/2020
Phys <- Water_Chem_Climate %>% 
  mutate(year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'18/'20")) %>% 
  filter(year %in% c("2018", "2020")) %>% 
  dplyr::select(c(site_id, year, month, okoregion, group, Temp_C, Turbidity, Conductivity_mS_m, pH, 
                  Water_Color_mgPt_l, Alkalinity_mmol_L, ANC_µEkv_L)) %>% 
  pivot_longer(cols= -c(site_id, year, month, group, okoregion), names_to = "Variable", values_to = "Measurement") %>% drop_na()


Phys$Variable <- factor(Phys$Variable,
                        levels = c("Temp_C", "Turbidity", "Conductivity_mS_m", "pH", 
                 "Water_Color_mgPt_l", "Alkalinity_mmol_L", "ANC_µEkv_L"),
                        labels = c(bquote('Temp'~ (C)),
                                   bquote('Turbidity'~ (NTU)),
                                   bquote('Conductivity'~ (mS~m^-1)),
                                   bquote('pH'),
                                   bquote('Water Color'~ (mgPt~L^-1)),
                                   bquote('Alkalinity'~ (mmol~L^-1)),             
                                   bquote('ANC'~ (µEkv~L^-1))))

Plot1 <- Phys %>% 
  ggplot(aes(x = month, y = Measurement, group = factor(year))) + 
  geom_point(size = 0.5, color ="gray70", alpha = 0.4) +
  scale_color_manual(values=c("#FFCC66", "#264EFF")) +
  scale_y_log10 () + 
  geom_smooth(aes(color = factor(year)), method = "gam", se = FALSE) +
  facet_grid(Variable~okoregion, scales = "free", labeller = label_parsed) +
  theme_bw() +
  xlab(NULL) +
  labs(color ="year") +
  theme(axis.text.x = element_text(size =6, angle = 45, hjust = 1)) 

ggsave("Figures/Phys_18_20.pdf", Plot1, width = 6.2, height = 10, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Phys_18_20.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Phys_18_20.jpeg")


# Phys: 2019/2021

Phys <- Water_Chem_Climate %>% 
  mutate(year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'19/'21")) %>% 
  filter(year %in% c("2019", "2021")) %>% 
  dplyr::select(c(site_id, year, month, okoregion, group, Temp_C, Turbidity, Conductivity_mS_m, pH, 
                  Water_Color_mgPt_l, Alkalinity_mmol_L, ANC_µEkv_L)) %>% 
  pivot_longer(cols= -c(site_id, year, month, group, okoregion), names_to = "Variable", values_to = "Measurement") %>% drop_na()


Phys$Variable <- factor(Phys$Variable,
                        levels = c("Temp_C", "Turbidity", "Conductivity_mS_m", "pH", 
                 "Water_Color_mgPt_l", "Alkalinity_mmol_L", "ANC_µEkv_L"),
                        labels = c(bquote('Temp'~ (C)),
                                   bquote('Turbidity'~ (NTU)),
                                   bquote('Conductivity'~ (mS~m^-1)),
                                   bquote('pH'),
                                   bquote('Water Color'~ (mgPt~L^-1)),
                                   bquote('Alkalinity'~ (mmol~L^-1)),             
                                   bquote('ANC'~ (µEkv~L^-1))))

Phys$okoregion <- factor(Phys$okoregion,
                        levels = c("Midt-Norge", "Nord-Norge ytre", "Vest", "Sorlandet"),
                        labels = c(bquote('Midt-Norge'),
                                   bquote("Nord-Norge-ytre"),
                                   bquote("Vest"),
                                   bquote("Sorlandet")))

Plot2 <- Phys %>% 
  ggplot(aes(x = month, y = Measurement, group = factor(year))) + 
  geom_point(size = 0.5, color ="gray70", alpha = 0.4) +
  scale_color_manual(values=c("#3399FF", "#FF8000")) +
  scale_y_log10 () + 
  geom_smooth(aes(color = factor(year)), method = "gam", se = FALSE) +
  facet_grid(Variable~okoregion, scales = "free", labeller = label_parsed) +
  theme_bw() +
  xlab(NULL) +
  labs(color ="year") +
  theme(axis.text.x = element_text(size =6, angle = 45, hjust = 1)) 

ggsave("Figures/Phys_19_21.pdf", Plot2, width = 6.5, height = 10, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Phys_19_21.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Phys_19_21.jpeg")


# Phys: 2018/2019/2020/2021

Phys <- Water_Chem_Climate %>% 
  mutate(year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'18/'19/'20/'21")) %>% 
  filter(year %in% c("2018", "2019", "2020", "2021")) %>% 
  dplyr::select(c(site_id, year, month, okoregion, group, Temp_C, Turbidity, Conductivity_mS_m, pH, 
                  Water_Color_mgPt_l, Alkalinity_mmol_L, ANC_µEkv_L)) %>% 
  pivot_longer(cols= -c(site_id, year, month, group, okoregion), names_to = "Variable", values_to = "Measurement") %>% drop_na()


Phys$Variable <- factor(Phys$Variable,
                        levels = c("Temp_C", "Turbidity", "Conductivity_mS_m", "pH", 
                 "Water_Color_mgPt_l", "Alkalinity_mmol_L", "ANC_µEkv_L"),
                        labels = c(bquote('Temp'~ (C)),
                                   bquote('Turbidity'~ (NTU)),
                                   bquote('Conductivity'~ (mS~m^-1)),
                                   bquote('pH'),
                                   bquote('Water Color'~ (mgPt~L^-1)),
                                   bquote('Alkalinity'~ (mmol~L^-1)),             
                                   bquote('ANC'~ (µEkv~L^-1))))

Plot3 <- Phys %>% 
  ggplot(aes(x = month, y = Measurement, group = factor(year))) + 
  geom_point(size = 0.5, color ="gray70", alpha = 0.4) +
  scale_color_manual(values=c("#FFCC66","#3399FF","#264EFF", "#FF8000")) +
  scale_y_log10 () + 
  geom_smooth(aes(color = factor(year)), method = "gam", se = FALSE) +
  facet_wrap(~Variable, scales = "free", labeller = label_parsed) +
  theme_bw() +
  xlab(NULL) +
  labs(color ="year") +
  theme(axis.text.x = element_text(size =8, angle = 45, hjust = 1)) 

ggsave("Figures/Phys_ALL.pdf", Plot3, width = 7, height = 5, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Phys_ALL.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Phys_ALL.jpeg")
```


## Metals2
```{r}
#Metals2
Water_Chem_Climate <- read_csv("Clean_Data/Water_Chem_Climate.csv")

# Metals2: 2018/2020
Metals2 <- Water_Chem_Climate %>% 
  mutate(year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'18/'20")) %>% 
  filter(year %in% c("2018", "2020")) %>% 
  dplyr::select(c(site_id, year, month, okoregion, group, Fe_ug_L, Al_ug_L, Al_il_ug_L, Al_l_ug_L, Al_r_ug_L)) %>% 
  pivot_longer(cols= -c(site_id, year, month, group, okoregion), names_to = "Variable", values_to = "Measurement") %>% drop_na()


Metals2$Variable <- factor(Metals2$Variable,
                        levels = c("Al_ug_L", "Al_il_ug_L", 
                                   "Al_l_ug_L", "Al_r_ug_L", "Fe_ug_L"),
                        labels = c(bquote('Al'~ (μg~L^-1)),
                                   bquote('Al- ikke labil'~ (μg~L^-1)),
                                   bquote('Al - labil'~ (μg~L^-1)),
                                   bquote('Al - reactive'~ (μg~L^-1)),
                                   bquote('Fe'~ (μg~L^-1))))


Plot1 <- Metals2 %>% 
  ggplot(aes(x = month, y = Measurement, group = factor(year))) + 
  geom_point(size = 0.5, color ="gray70", alpha = 0.4) +
  scale_color_manual(values=c("#FFCC66", "#264EFF")) +
  scale_y_log10 () + 
  geom_smooth(aes(color = factor(year)), method = "gam", se = FALSE) +
  facet_grid(Variable~okoregion, scales = "free", labeller = label_parsed) +
  theme_bw() +
  xlab(NULL) +
  labs(color ="year") +
  theme(axis.text.x = element_text(size =6, angle = 45, hjust = 1)) 

ggsave("Figures/Metals2_18_20.pdf", Plot1, width = 6.2, height = 6, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Metals2_18_20.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Metals2_18_20.jpeg")


# Metals: 2019/2021

Metals2 <- Water_Chem_Climate %>% 
  mutate(year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'19/'21")) %>% 
  filter(year %in% c("2019", "2021")) %>% 
  dplyr::select(c(site_id, year, month, okoregion, group, Fe_ug_L, Al_ug_L, Al_il_ug_L, Al_l_ug_L, Al_r_ug_L)) %>% 
  pivot_longer(cols= -c(site_id, year, month, group, okoregion), names_to = "Variable", values_to = "Measurement") %>% drop_na()


Metals2$Variable <- factor(Metals2$Variable,
                        levels = c("Al_ug_L", "Al_il_ug_L", 
                                   "Al_l_ug_L", "Al_r_ug_L", "Fe_ug_L"),
                        labels = c(bquote('Al'~ (μg~L^-1)),
                                   bquote('Al- ikke labil'~ (μg~L^-1)),
                                   bquote('Al - labil'~ (μg~L^-1)),
                                   bquote('Al - reactive'~ (μg~L^-1)),
                                   bquote('Fe'~ (μg~L^-1))))

Metals2$okoregion <- factor(Metals2$okoregion,
                        levels = c("Midt-Norge", "Nord-Norge ytre", "Vest", "Sorlandet"),
                        labels = c(bquote('Midt-Norge'),
                                   bquote("Nord-Norge-ytre"),
                                   bquote("Vest"),
                                   bquote("Sorlandet")))

Plot2 <- Metals2 %>% 
  ggplot(aes(x = month, y = Measurement, group = factor(year))) + 
  geom_point(size = 0.5, color ="gray70", alpha = 0.4) +
  scale_color_manual(values=c("#3399FF", "#FF8000")) +
  scale_y_log10 () + 
  geom_smooth(aes(color = factor(year)), method = "gam", se = FALSE) +
  facet_grid(Variable~okoregion, scales = "free", labeller = label_parsed) +
  theme_bw() +
  xlab(NULL) +
  labs(color ="year") +
  theme(axis.text.x = element_text(size =6, angle = 45, hjust = 1)) 

ggsave("Figures/Metals2_19_21.pdf", Plot2, width = 6.5, height = 6, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Metals2_19_21.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Metals2_19_21.jpeg")


# Metals: 2018/2019/2020/2021

Metals2 <- Water_Chem_Climate %>% 
  mutate(year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'18/'19/'20/'21")) %>% 
  filter(year %in% c("2018", "2019", "2020", "2021")) %>% 
  dplyr::select(c(site_id, year, month, okoregion, group, Fe_ug_L, Al_ug_L, Al_il_ug_L, Al_l_ug_L, Al_r_ug_L)) %>% 
  pivot_longer(cols= -c(site_id, year, month, group, okoregion), names_to = "Variable", values_to = "Measurement") %>% drop_na()


Metals2$Variable <- factor(Metals2$Variable,
                        levels = c("Al_ug_L", "Al_il_ug_L", 
                                   "Al_l_ug_L", "Al_r_ug_L", "Fe_ug_L"),
                        labels = c(bquote('Al'~ (μg~L^-1)),
                                   bquote('Al- ikke labil'~ (μg~L^-1)),
                                   bquote('Al - labil'~ (μg~L^-1)),
                                   bquote('Al - reactive'~ (μg~L^-1)),
                                   bquote('Fe'~ (μg~L^-1))))
Plot3 <- Metals2 %>% 
  ggplot(aes(x = month, y = Measurement, group = factor(year))) + 
  geom_point(size = 0.5, color ="gray70", alpha = 0.4) +
  scale_color_manual(values=c("#FFCC66","#3399FF","#264EFF", "#FF8000")) +
  scale_y_log10 () + 
  geom_smooth(aes(color = factor(year)), method = "gam", se = FALSE) +
  facet_wrap(~Variable, scales = "free", labeller = label_parsed) +
  theme_bw() +
  xlab(NULL) +
  labs(color ="year") +
  theme(axis.text.x = element_text(size =8, angle = 45, hjust = 1)) 

ggsave("Figures/Metals2_ALL.pdf", Plot3, width = 7, height = 5, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Metals2_ALL.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Metals2_ALL.jpeg")
```


## Ions

```{r}
# Ions
Water_Chem_Climate <- read_csv("Clean_Data/Water_Chem_Climate.csv")

# Ions: 2018/2020
Ions <- Water_Chem_Climate %>% 
  mutate(year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'18/'20")) %>% 
  filter(year %in% c("2018", "2020")) %>% 
  dplyr::select(c(site_id, year, month, okoregion, group, Mg_mg_L, K_mg_L, Ca_mg_L, SO4_mg_L, Na_mg_L)) %>% 
  pivot_longer(cols= -c(site_id, year, month, group, okoregion), names_to = "Variable", values_to = "Measurement") %>% drop_na()


Ions$Variable <- factor(Ions$Variable,
                        levels = c("Mg_mg_L", "K_mg_L", "Ca_mg_L", "SO4_mg_L", "Na_mg_L"),
                        labels = c(bquote('Mg'~ (mg~L^-1)),
                                   bquote('K'~ (mg~L^-1)),
                                   bquote('Ca'~ (mg~L^-1)),
                                   bquote('SO'[4]~ (mg~L^-1)),
                                   bquote('Na'~ (mg~L^-1))))


Plot1 <- Ions %>% 
  ggplot(aes(x = month, y = Measurement, group = factor(year))) + 
  geom_point(size = 0.5, color ="gray70", alpha = 0.4) +
  scale_color_manual(values=c("#FFCC66", "#264EFF")) +
  scale_y_log10 () + 
  geom_smooth(aes(color = factor(year)), method = "gam", se = FALSE) +
  facet_grid(Variable~okoregion, scales = "free", labeller = label_parsed) +
  theme_bw() +
  xlab(NULL) +
  labs(color ="year") +
  theme(axis.text.x = element_text(size =6, angle = 45, hjust = 1)) 

ggsave("Figures/Ions_18_20.pdf", Plot1, width = 6.2, height = 6, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Ions_18_20.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Ions_18_20.jpeg")


# Ions 2019/2021

Ions <- Water_Chem_Climate %>% 
  mutate(year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'19/'21")) %>% 
  filter(year %in% c("2019", "2021")) %>% 
  dplyr::select(c(site_id, year, month, okoregion, group, Mg_mg_L, K_mg_L, Ca_mg_L, SO4_mg_L, Na_mg_L)) %>% 
  pivot_longer(cols= -c(site_id, year, month, group, okoregion), names_to = "Variable", values_to = "Measurement") %>% drop_na()


Ions$Variable <- factor(Ions$Variable,
                        levels = c("Mg_mg_L", "K_mg_L", "Ca_mg_L", "SO4_mg_L", "Na_mg_L"),
                        labels = c(bquote('Mg'~ (mg~L^-1)),
                                   bquote('K'~ (mg~L^-1)),
                                   bquote('Ca'~ (mg~L^-1)),
                                   bquote('SO'[4]~ (mg~L^-1)),
                                   bquote('Na'~ (mg~L^-1))))

Ions$okoregion <- factor(Ions$okoregion,
                        levels = c("Midt-Norge", "Nord-Norge ytre", "Vest", "Sorlandet"),
                        labels = c(bquote('Midt-Norge'),
                                   bquote("Nord-Norge-ytre"),
                                   bquote("Vest"),
                                   bquote("Sorlandet")))

Plot2 <- Ions %>% 
  ggplot(aes(x = month, y = Measurement, group = factor(year))) + 
  geom_point(size = 0.5, color ="gray70", alpha = 0.4) +
  scale_color_manual(values=c("#3399FF", "#FF8000")) +
  scale_y_log10 () + 
  geom_smooth(aes(color = factor(year)), method = "gam", se = FALSE) +
  facet_grid(Variable~okoregion, scales = "free", labeller = label_parsed) +
  theme_bw() +
  xlab(NULL) +
  labs(color ="year") +
  theme(axis.text.x = element_text(size =6, angle = 45, hjust = 1)) 

ggsave("Figures/Ions_19_21.pdf", Plot2, width = 6.5, height = 6, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Ions_19_21.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Ions_19_21.jpeg")


# Ions: 2018/2019/2020/2021

Ions <- Water_Chem_Climate %>% 
  mutate(year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'18/'19/'20/'21")) %>% 
  filter(year %in% c("2018", "2019", "2020", "2021")) %>% 
  dplyr::select(c(site_id, year, month, okoregion, group, Mg_mg_L, K_mg_L, Ca_mg_L, SO4_mg_L, Na_mg_L)) %>% 
  pivot_longer(cols= -c(site_id, year, month, group, okoregion), names_to = "Variable", values_to = "Measurement") %>% drop_na()


Ions$Variable <- factor(Ions$Variable,
                        levels = c("Mg_mg_L", "K_mg_L", "Ca_mg_L", "SO4_mg_L", "Na_mg_L"),
                        labels = c(bquote('Mg'~ (mg~L^-1)),
                                   bquote('K'~ (mg~L^-1)),
                                   bquote('Ca'~ (mg~L^-1)),
                                   bquote('SO'[4]~ (mg~L^-1)),
                                   bquote('Na'~ (mg~L^-1))))

Plot3 <- Ions %>% 
  ggplot(aes(x = month, y = Measurement, group = factor(year))) + 
  geom_point(size = 0.5, color ="gray70", alpha = 0.4) +
  scale_color_manual(values=c("#FFCC66","#3399FF","#264EFF", "#FF8000")) +
  scale_y_log10 () + 
  geom_smooth(aes(color = factor(year)), method = "gam", se = FALSE) +
  facet_wrap(~Variable, scales = "free", labeller = label_parsed) +
  theme_bw() +
  xlab(NULL) +
  labs(color ="year") +
  theme(axis.text.x = element_text(size =8, angle = 45, hjust = 1)) 

ggsave("Figures/Ions_ALL.pdf", Plot3, width = 7, height = 5, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Ions_ALL.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Ions_ALL.jpeg")
```



## Nutrients
```{r}
# Nutrients
Water_Chem_Climate <- read_csv("Clean_Data/Water_Chem_Climate.csv")

# Nutrients: 2018/2020
Nutrients <- Water_Chem_Climate %>% 
  mutate(year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'18/'20")) %>% 
  filter(year %in% c("2018", "2020")) %>% 
  dplyr::select(c(site_id, year, month, okoregion, group, TotP_ug_L, TotN_ug_L, PO4_ug_L, NO3_ug_L, SiO2_mg_L)) %>% 
  pivot_longer(cols= -c(site_id, year, month, group, okoregion), names_to = "Variable", values_to = "Measurement") %>% drop_na()


Nutrients$Variable <- factor(Nutrients$Variable,
                        levels = c("TotP_ug_L", "TotN_ug_L", "PO4_ug_L", 
                                   "NO3_ug_L", "SiO2_mg_L"),
                        labels = c(bquote('TotP'~ (μg~L^-1)),
                                   bquote('TotN'~ (μg~L^-1)),
                                   bquote('PO'[4]~ (μg~L^-1)),
                                   bquote('NO'[3]~ (μg~L^-1)),
                                   bquote('SiO'[2]~ (mg~L^-1))))


Plot1 <- Nutrients %>% 
  ggplot(aes(x = month, y = Measurement, group = factor(year))) + 
  geom_point(size = 0.5, color ="gray70", alpha = 0.4) +
  scale_color_manual(values=c("#FFCC66", "#264EFF")) +
  scale_y_log10 () + 
  geom_smooth(aes(color = factor(year)), method = "gam", se = FALSE) +
  facet_grid(Variable~okoregion, scales = "free", labeller = label_parsed) +
  theme_bw() +
  xlab(NULL) +
  labs(color ="year") +
  theme(axis.text.x = element_text(size =6, angle = 45, hjust = 1)) 

ggsave("Figures/Nutrients_18_20.pdf", Plot1, width = 6.2, height = 6, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Nutrients_18_20.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Nutrients_18_20.jpeg")


# Nutrients 2019/2021

Nutrients <- Water_Chem_Climate %>% 
  mutate(year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'19/'21")) %>% 
  filter(year %in% c("2019", "2021")) %>% 
  dplyr::select(c(site_id, year, month, okoregion, group, TotP_ug_L, TotN_ug_L, PO4_ug_L, NO3_ug_L, SiO2_mg_L)) %>% 
  pivot_longer(cols= -c(site_id, year, month, group, okoregion), names_to = "Variable", values_to = "Measurement") %>% drop_na()


Nutrients$Variable <- factor(Nutrients$Variable,
                        levels = c("TotP_ug_L", "TotN_ug_L", 
                                   "PO4_ug_L", "NO3_ug_L", "SiO2_mg_L"),
                        labels = c(bquote('TotP'~ (μg~L^-1)),
                                   bquote('TotN'~ (μg~L^-1)),
                                   bquote('PO'[4]~ (μg~L^-1)),
                                   bquote('NO'[3]~ (μg~L^-1)),
                                   bquote('SiO'[2]~ (mg~L^-1))))

Nutrients$okoregion <- factor(Nutrients$okoregion,
                        levels = c("Midt-Norge", "Nord-Norge ytre", "Vest", "Sorlandet"),
                        labels = c(bquote('Midt-Norge'),
                                   bquote("Nord-Norge-ytre"),
                                   bquote("Vest"),
                                   bquote("Sorlandet")))

Plot2 <- Nutrients %>% 
  ggplot(aes(x = month, y = Measurement, group = factor(year))) + 
  geom_point(size = 0.5, color ="gray70", alpha = 0.4) +
  scale_color_manual(values=c("#3399FF", "#FF8000")) +
  scale_y_log10 () + 
  geom_smooth(aes(color = factor(year)), method = "gam", se = FALSE) +
  facet_grid(Variable~okoregion, scales = "free", labeller = label_parsed) +
  theme_bw() +
  xlab(NULL) +
  labs(color ="year") +
  theme(axis.text.x = element_text(size =6, angle = 45, hjust = 1)) 

ggsave("Figures/Nutrients_19_21.pdf", Plot2, width = 6.5, height = 6, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Nutrients_19_21.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Nutrients_19_21.jpeg")


# Nutrients: 2018/2019/2020/2021

Nutrients <- Water_Chem_Climate %>% 
  mutate(year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'18/'19/'20/'21")) %>% 
  filter(year %in% c("2018", "2019", "2020", "2021")) %>% 
  dplyr::select(c(site_id, year, month, okoregion, group, TotP_ug_L, TotN_ug_L, PO4_ug_L, NO3_ug_L, SiO2_mg_L)) %>% 
  pivot_longer(cols= -c(site_id, year, month, group, okoregion), names_to = "Variable", values_to = "Measurement") %>% drop_na()


Nutrients$Variable <- factor(Nutrients$Variable,
                        levels = c("TotP_ug_L", "TotN_ug_L", 
                                   "PO4_ug_L", "NO3_ug_L", "SiO2_mg_L"),
                        labels = c(bquote('TotP'~ (μg~L^-1)),
                                   bquote('TotN'~ (μg~L^-1)),
                                   bquote('PO'[4]~ (μg~L^-1)),
                                   bquote('NO'[3]~ (μg~L^-1)),
                                   bquote('SiO'[2]~ (mg~L^-1))))

Plot3 <- Nutrients %>% 
  ggplot(aes(x = month, y = Measurement, group = factor(year))) + 
  geom_point(size = 0.5, color ="gray70", alpha = 0.4) +
  scale_color_manual(values=c("#FFCC66","#3399FF","#264EFF", "#FF8000")) +
  scale_y_log10 () + 
  geom_smooth(aes(color = factor(year)), method = "gam", se = FALSE) +
  facet_wrap(~Variable, scales = "free", labeller = label_parsed) +
  theme_bw() +
  xlab(NULL) +
  labs(color ="year") +
  theme(axis.text.x = element_text(size =8, angle = 45, hjust = 1)) 

ggsave("Figures/Nutrients_ALL.pdf", Plot3, width = 7, height = 5, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Nutrients_ALL.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Nutrients_ALL.jpeg")
```



## Carbon
```{r}
# Carbon
Water_Chem_Climate <- read_csv("Clean_Data/Water_Chem_Climate.csv")

# Carbon: 2018/2020
Carbon <- Water_Chem_Climate %>% 
  mutate(year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'18/'20")) %>% 
  filter(year %in% c("2018", "2020")) %>% 
  dplyr::select(c(site_id, year, month, okoregion, group, DOC_mg_L, TOC_mg_L)) %>% 
  pivot_longer(cols= -c(site_id, year, month, group, okoregion), names_to = "Variable", values_to = "Measurement") %>% drop_na()


Carbon$Variable <- factor(Carbon$Variable, levels = c("DOC_mg_L", "TOC_mg_L"),
                          labels = c(bquote('DOC'~ (mg~L^-1)), 
                                     bquote('TOC'~ (mg~L^-1))))

Plot1 <- Carbon %>% 
  ggplot(aes(x = month, y = Measurement, group = factor(year))) + 
  geom_point(size = 0.5, color ="gray70", alpha = 0.4) +
  scale_color_manual(values=c("#FFCC66", "#264EFF")) +
  scale_y_log10 () + 
  geom_smooth(aes(color = factor(year)), method = "gam", se = FALSE) +
  facet_grid(Variable~okoregion, scales = "free", labeller = label_parsed) +
  theme_bw() +
  xlab(NULL) +
  labs(color ="year") +
  theme(axis.text.x = element_text(size =6, angle = 45, hjust = 1)) 

ggsave("Figures/Carbon_18_20.pdf", Plot1, width = 6.2, height = 3, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Carbon_18_20.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Carbon_18_20.jpeg")


# Carbon 2019/2021

Carbon <- Water_Chem_Climate %>% 
  mutate(year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'19/'21")) %>% 
  filter(year %in% c("2019", "2021")) %>% 
  dplyr::select(c(site_id, year, month, okoregion, group, DOC_mg_L, TOC_mg_L)) %>% 
  pivot_longer(cols= -c(site_id, year, month, group, okoregion), names_to = "Variable", values_to = "Measurement") %>% drop_na()


Carbon$Variable <- factor(Carbon$Variable, levels = c("DOC_mg_L", "TOC_mg_L"),
                          labels = c(bquote('DOC'~ (mg~L^-1)), 
                                     bquote('TOC'~ (mg~L^-1))))

Carbon$okoregion <- factor(Carbon$okoregion,
                        levels = c("Midt-Norge", "Nord-Norge ytre", "Vest", "Sorlandet"),
                        labels = c(bquote('Midt-Norge'),
                                   bquote("Nord-Norge-ytre"),
                                   bquote("Vest"),
                                   bquote("Sorlandet")))

Plot2 <- Carbon %>% 
  ggplot(aes(x = month, y = Measurement, group = factor(year))) + 
  geom_point(size = 0.5, color ="gray70", alpha = 0.4) +
  scale_color_manual(values=c("#3399FF", "#FF8000")) +
  scale_y_log10 () + 
  geom_smooth(aes(color = factor(year)), method = "gam", se = FALSE) +
  facet_grid(Variable~okoregion, scales = "free", labeller = label_parsed) +
  theme_bw() +
  xlab(NULL) +
  labs(color ="year") +
  theme(axis.text.x = element_text(size =6, angle = 45, hjust = 1)) 

ggsave("Figures/Carbon_19_21.pdf", Plot2, width = 6.5, height = 3, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Carbon_19_21.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Carbon_19_21.jpeg")


# Carbon: 2018/2019/2020/2021

Carbon <- Water_Chem_Climate %>% 
  mutate(year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'18/'19/'20/'21")) %>% 
  filter(year %in% c("2018", "2019", "2020", "2021")) %>% 
  dplyr::select(c(site_id, year, month, okoregion, group, DOC_mg_L, TOC_mg_L)) %>% 
  pivot_longer(cols= -c(site_id, year, month, group, okoregion), names_to = "Variable", values_to = "Measurement") %>% drop_na()

Carbon$Variable <- factor(Carbon$Variable, levels = c("DOC_mg_L", "TOC_mg_L"),
                          labels = c(bquote('DOC'~ (mg~L^-1)), 
                                     bquote('TOC'~ (mg~L^-1))))

Plot3 <- Carbon %>% 
  ggplot(aes(x = month, y = Measurement, group = factor(year))) + 
  geom_point(size = 0.5, color ="gray70", alpha = 0.4) +
  scale_color_manual(values=c("#FFCC66","#3399FF","#264EFF", "#FF8000")) +
  scale_y_log10 () + 
  geom_smooth(aes(color = factor(year)), method = "gam", se = FALSE) +
  facet_wrap(~Variable, scales = "free", labeller = label_parsed) +
  theme_bw() +
  xlab(NULL) +
  labs(color ="year") +
  theme(axis.text.x = element_text(size =8, angle = 45, hjust = 1)) 

ggsave("Figures/Carbon_ALL.pdf", Plot3, width = 7, height = 2.5, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Carbon_ALL.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Carbon_ALL.jpeg")
```




# Water Chemistry by Elevation

```{r}
#Phys

Phys <- Water_Chem_Climate %>% 
  dplyr::select(c(site_id, Date, mean_elevation, Temp_C, Turbidity, Conductivity_mS_m, pH, 
                  Water_Color_mgPt_l, Alkalinity_mmol_L, ANC_µEkv_L)) %>% 
  pivot_longer(cols= -c(site_id, Date, mean_elevation), names_to = "Variable", values_to = "Measurement") %>% 
  mutate(Elevation = ifelse(mean_elevation < 900, "low", "high")) %>% 
  drop_na(Elevation)


Phys$Variable <- factor(Phys$Variable,
                        levels = c("Temp_C", "Turbidity", "Conductivity_mS_m", "pH", 
                 "Water_Color_mgPt_l", "Alkalinity_mmol_L", "ANC_µEkv_L"),
                        labels = c(bquote('Temp'~ (C)),
                                   bquote('Turbidity'~ (NTU)),
                                   bquote('Conductivity'~ (mS~m^-1)),
                                   bquote('pH'),
                                   bquote('Water Color'~ (mgPt~L^-1)),
                                   bquote('Alkalinity'~ (mmol~L^-1)),             
                                   bquote('ANC'~ (µEkv~L^-1))))

Plot1 <- Phys %>% 
  ggplot(aes(x = Date, y = Measurement)) + 
  geom_point(size = 0.5, color ="gray70", alpha = 0.4) +
  scale_color_manual(values = c("darkblue","coral4")) +
  scale_y_log10 () + 
  geom_smooth(aes(color = Elevation), method = "gam", se = FALSE) +
  facet_wrap(~ Variable, scales = "free", labeller = label_parsed) +
  theme_bw() +
  xlab(NULL) 

ggsave("Figures/Phys.pdf", Plot1, width = 9, height = 5.5, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Phys.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Phys.jpeg")



# Metals
Metals <- Water_Chem_Climate %>% 
  dplyr::select(c(site_id, Date, mean_elevation, Fe_ug_L, Cd_ug_L, Cu_ug_L, Cr_ug_L, Pb_ug_L, Ni_ug_L, Zn_ug_L)) %>% 
  pivot_longer(cols= -c(site_id, Date, mean_elevation), names_to = "Variable", values_to = "Measurement")  %>%
  mutate(Elevation = ifelse(mean_elevation < 900, "low", "high")) %>% 
  drop_na(Elevation)

Metals$Variable <- factor(Metals$Variable,
                        levels = c("Fe_ug_L", "Cd_ug_L", "Cr_ug_L", "Cu_ug_L",
                                   "Pb_ug_L", "Ni_ug_L", "Zn_ug_L"),
                        labels = c(bquote('Fe'~ (μg~L^-1)),
                                   bquote('Cd'~ (μg~L^-1)),
                                   bquote('Cr'~ (μg~L^-1)),
                                   bquote('Cu'~ (μg~L^-1)),
                                   bquote('Pb'~ (μg~L^-1)),
                                   bquote('Ni'~ (μg~L^-1)),             
                                   bquote('Zn'~ (μg~L^-1))))

Plot2 <- Metals %>%  
  ggplot(aes(x = Date, y = Measurement)) + 
  geom_point(size = 0.5, color ="gray70", alpha = 0.4) +
  scale_y_log10 () + 
  scale_color_manual(values = c("darkblue","coral4")) +
  geom_smooth(aes(color = Elevation), method = "gam", se = FALSE) +
  facet_wrap(~ Variable, scales = "free", labeller = label_parsed) +
  theme_bw() +
  xlab(NULL) 

ggsave("Figures/Metals.pdf", Plot2, width = 9, height = 5.5, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Metals.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Metals.jpeg")



#Metals
Metals2 <- Water_Chem_Climate %>% 
  dplyr::select(c(site_id, Date, mean_elevation, Al_ug_L, Al_il_ug_L, Al_l_ug_L, Al_r_ug_L)) %>% 
  pivot_longer(cols= -c(site_id, Date, mean_elevation), names_to = "Variable", values_to = "Measurement") %>% 
  mutate(Elevation = ifelse(mean_elevation < 900, "low", "high")) %>% 
  drop_na(Elevation)

Metals2$Variable <- factor(Metals2$Variable,
                        levels = c("Al_ug_L", "Al_il_ug_L", "Al_l_ug_L", "Al_r_ug_L"),
                        labels = c(bquote('Al'~ (μg~L^-1)),
                                   bquote('Al- ikke labil'~ (μg~L^-1)),
                                   bquote('Al - labil'~ (μg~L^-1)),
                                   bquote('Al - reactive'~ (μg~L^-1))))

Plot3 <- Metals2 %>% 
  ggplot(aes(x = Date, y = Measurement)) + 
  geom_point(size = 0.5, color ="gray70", alpha = 0.4) +
  scale_color_manual(values = c("darkblue","coral4")) +
  scale_y_log10 () + 
  geom_smooth(aes(color = Elevation), method = "gam", se = FALSE) +
  facet_wrap(~ Variable, scales = "free", labeller = label_parsed) +
  theme_bw() +
  xlab(NULL) 

ggsave("Figures/Metals2.pdf", Plot3, width = 7, height = 5, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Metals2.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Metals2.jpeg")


#Ions
Ions <- Water_Chem_Climate %>% 
  dplyr::select(c(site_id, Date, mean_elevation, Mg_mg_L, K_mg_L, Ca_mg_L, SO4_mg_L, Na_mg_L)) %>% 
  pivot_longer(cols= -c(site_id, Date, mean_elevation), names_to = "Variable", values_to = "Measurement") %>% 
  mutate(Elevation = ifelse(mean_elevation < 900, "low", "high")) %>% 
  drop_na(Elevation)

Ions$Variable <- factor(Ions$Variable,
                        levels = c("Mg_mg_L", "K_mg_L", "Ca_mg_L", "SO4_mg_L", "Na_mg_L"),
                        labels = c(bquote('Mg'~ (mg~L^-1)),
                                   bquote('K'~ (mg~L^-1)),
                                   bquote('Ca'~ (mg~L^-1)),
                                   bquote('SO'[4]~ (mg~L^-1)),
                                   bquote('Na'~ (mg~L^-1))))

Plot4 <- Ions %>% ggplot(aes(x = Date, y = Measurement)) + 
  geom_point(size = 0.5, color ="gray70", alpha = 0.4) +
  scale_color_manual(values = c("darkblue","coral4")) +
  scale_y_log10 () + 
  geom_smooth(aes(color = Elevation), method = "gam", se = FALSE) +
  facet_wrap(~ Variable, scales = "free", labeller = label_parsed) +
  theme_bw() +
  xlab(NULL) 

ggsave("Figures/Ions.pdf", Plot4, width = 8, height = 3.75, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Ions.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Ions.jpeg")


#Nutrients

Nutrients <- Water_Chem_Climate %>% 
  dplyr::select(c(site_id, Date, mean_elevation, TotP_ug_L, TotN_ug_L, PO4_ug_L, NO3_ug_L, SiO2_mg_L)) %>% 
  pivot_longer(cols= -c(site_id, Date, mean_elevation), names_to = "Variable", values_to = "Measurement") %>% 
  mutate(Elevation = ifelse(mean_elevation < 900, "low", "high")) %>% 
  drop_na(Elevation)

Nutrients$Variable <- factor(Nutrients$Variable,
                        levels = c("TotP_ug_L", "TotN_ug_L", "PO4_ug_L", "NO3_ug_L", "SiO2_mg_L"),
                        labels = c(bquote('TotP'~ (μg~L^-1)),
                                   bquote('TotN'~ (μg~L^-1)),
                                   bquote('PO'[4]~ (μg~L^-1)),
                                   bquote('NO'[3]~ (μg~L^-1)),
                                   bquote('SiO'[2]~ (mg~L^-1))))
  
Plot5 <- Nutrients %>% 
  ggplot(aes(x = Date, y = Measurement)) + 
  geom_point(size = 0.5, color ="gray70", alpha = 0.4) +
  scale_color_manual(values = c("darkblue","coral4")) +
  scale_y_log10 () + 
  geom_smooth(aes(color = Elevation), method = "gam", se = FALSE) +
  facet_wrap(~ Variable, scales = "free", labeller = label_parsed) +
  theme_bw() +
  xlab(NULL) 

ggsave("Figures/Nutrients.pdf", Plot5, width = 9, height = 5, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Nutrients.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Nutrients.jpeg")


#Carbon
Carbon <- Water_Chem_Climate %>% 
  dplyr::select(c(site_id, Date, mean_elevation, DOC_mg_L, TOC_mg_L)) %>% 
  pivot_longer(cols= -c(site_id, Date, mean_elevation), names_to = "Variable", values_to = "Measurement") %>% 
  mutate(Elevation = ifelse(mean_elevation < 900, "low", "high")) %>% 
  drop_na(Elevation)
  
Carbon$Variable <- factor(Carbon$Variable, levels = c("DOC_mg_L", "TOC_mg_L"),
                          labels = c(bquote('DOC'~ (mg~L^-1)), 
                                     bquote('TOC'~ (mg~L^-1))))

Plot6 <- Carbon %>% 
  ggplot(aes(x = Date, y = Measurement)) + 
  geom_point(size = 0.5, color ="gray70", alpha = 0.4) +
  scale_color_manual(values = c("darkblue","coral4")) +
  scale_y_log10 () + 
  geom_smooth(aes(color = Elevation), method = "gam", se = FALSE) +
  facet_wrap(~ Variable, scales = "free", labeller = label_parsed) +
  theme_bw() +
  xlab(NULL) 

ggsave("Figures/Carbon.pdf", Plot6, width = 6, height = 2, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Carbon.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Carbon.jpeg")
```

# Waterchem colors by Land Cover groupings. 
```{r}
names(Water_Chem_Climate)
#Phys
Phys <- Water_Chem_Climate %>% 
  dplyr::select(c(site_id, Date, coniferous_forest, Temp_C, Turbidity, Conductivity_mS_m, pH, 
                  Water_Color_mgPt_l, Alkalinity_mmol_L, ANC_µEkv_L)) %>% 
  pivot_longer(cols= -c(site_id, Date, coniferous_forest), names_to = "Variable", values_to = "Measurement") %>% 
  mutate(Coniferous = ifelse(coniferous_forest >20, "Coniferous", "Other")) %>% 
  #mutate(Coniferous = "Other") %>% 
  #mutate(Coniferous = ifelse(coniferous_forest > 40, "Coniferous", Coniferous)) %>% 
  #mutate(Coniferous = ifelse(sparse_vegetation > 40, "Sparse", Coniferous)) %>% 
  drop_na(Coniferous)


Phys$Variable <- factor(Phys$Variable,
                        levels = c("Temp_C", "Turbidity", "Conductivity_mS_m", "pH", 
                 "Water_Color_mgPt_l", "Alkalinity_mmol_L", "ANC_µEkv_L"),
                        labels = c(bquote('Temp'~ (C)),
                                   bquote('Turbidity'~ (NTU)),
                                   bquote('Conductivity'~ (mS~m^-1)),
                                   bquote('pH'),
                                   bquote('Water Color'~ (mgPt~L^-1)),
                                   bquote('Alkalinity'~ (mmol~L^-1)),             
                                   bquote('ANC'~ (µEkv~L^-1))))

Plot1 <- Phys %>% 
  ggplot(aes(x = Date, y = Measurement)) + 
  geom_point(size = 0.5, color ="gray75", alpha = 0.4) +
  scale_color_manual(values = c("chartreuse4","cornflowerblue")) +
  scale_y_log10 () + 
  geom_smooth(aes(color = Coniferous), method = "gam", se = FALSE) +
  facet_wrap(~ Variable, scales = "free", labeller = label_parsed) +
  theme_bw() +
  xlab(NULL) 

ggsave("Figures/Phys_lc.pdf", Plot1, width = 9, height = 5.5, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Phys_lc.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Phys_lc.jpeg")

#Metals
Metals <- Water_Chem_Climate %>% 
  dplyr::select(c(site_id, Date, coniferous_forest, Fe_ug_L, Cd_ug_L, Cu_ug_L, Cr_ug_L, Pb_ug_L, Ni_ug_L, Zn_ug_L)) %>% 
  pivot_longer(cols= -c(site_id, Date, coniferous_forest), names_to = "Variable", values_to = "Measurement")  %>%
  mutate(Coniferous = ifelse(coniferous_forest >20, "Coniferous", "Other")) %>% 
  drop_na(Coniferous)

Metals$Variable <- factor(Metals$Variable,
                        levels = c("Fe_ug_L", "Cd_ug_L", "Cr_ug_L", "Cu_ug_L",
                                   "Pb_ug_L", "Ni_ug_L", "Zn_ug_L"),
                        labels = c(bquote('Fe'~ (μg~L^-1)),
                                   bquote('Cd'~ (μg~L^-1)),
                                   bquote('Cr'~ (μg~L^-1)),
                                   bquote('Cu'~ (μg~L^-1)),
                                   bquote('Pb'~ (μg~L^-1)),
                                   bquote('Ni'~ (μg~L^-1)),             
                                   bquote('Zn'~ (μg~L^-1))))

Plot2 <- Metals %>%  
  ggplot(aes(x = Date, y = Measurement)) + 
  geom_point(size = 0.5, color ="gray75", alpha = 0.4) +
  scale_y_log10 () + 
  scale_color_manual(values = c("chartreuse4","cornflowerblue")) +
  geom_smooth(aes(color = Coniferous), method = "gam", se = FALSE) +
  facet_wrap(~ Variable, scales = "free", labeller = label_parsed) +
  theme_bw() +
  xlab(NULL) 

ggsave("Figures/Metals_lc.pdf", Plot2, width = 9, height = 5.5, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Metals_lc.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Metals_lc.jpeg")


#Metals
Metals2 <- Water_Chem_Climate %>% 
  dplyr::select(c(site_id, Date, coniferous_forest, Al_ug_L, Al_il_ug_L, Al_l_ug_L, Al_r_ug_L)) %>% 
  pivot_longer(cols= -c(site_id, Date, coniferous_forest), names_to = "Variable", values_to = "Measurement") %>% 
  mutate(Coniferous = ifelse(coniferous_forest >20, "Coniferous", "Other")) %>% 
  drop_na(Coniferous)

Metals2$Variable <- factor(Metals2$Variable,
                        levels = c("Al_ug_L", "Al_il_ug_L", "Al_l_ug_L", "Al_r_ug_L"),
                        labels = c(bquote('Al'~ (μg~L^-1)),
                                   bquote('Al- ikke labil'~ (μg~L^-1)),
                                   bquote('Al - labil'~ (μg~L^-1)),
                                   bquote('Al - reactive'~ (μg~L^-1))))

Plot3 <- Metals2 %>% 
  ggplot(aes(x = Date, y = Measurement)) + 
  geom_point(size = 0.5, color ="gray75", alpha = 0.4) +
  scale_color_manual(values = c("chartreuse4","cornflowerblue")) +
  scale_y_log10 () + 
  geom_smooth(aes(color = Coniferous), method = "gam", se = FALSE) +
  facet_wrap(~ Variable, scales = "free", labeller = label_parsed) +
  theme_bw() +
  xlab(NULL) 

ggsave("Figures/Metals2_lc.pdf", Plot3, width = 7, height = 5, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Metals2_lc.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Metals2_lc.jpeg")


#Ions
Ions <- Water_Chem_Climate %>% 
  dplyr::select(c(site_id, Date, coniferous_forest, Mg_mg_L, K_mg_L, Ca_mg_L, SO4_mg_L, Na_mg_L)) %>% 
  pivot_longer(cols= -c(site_id, Date, coniferous_forest), names_to = "Variable", values_to = "Measurement") %>% 
  mutate(Coniferous = ifelse(coniferous_forest >20, "Coniferous", "Other")) %>% 
  drop_na(Coniferous)

Ions$Variable <- factor(Ions$Variable,
                        levels = c("Mg_mg_L", "K_mg_L", "Ca_mg_L", "SO4_mg_L", "Na_mg_L"),
                        labels = c(bquote('Mg'~ (mg~L^-1)),
                                   bquote('K'~ (mg~L^-1)),
                                   bquote('Ca'~ (mg~L^-1)),
                                   bquote('SO'[4]~ (mg~L^-1)),
                                   bquote('Na'~ (mg~L^-1))))

Plot4 <- Ions %>% ggplot(aes(x = Date, y = Measurement)) + 
  geom_point(size = 0.5, color ="gray75", alpha = 0.4) +
  scale_color_manual(values = c("chartreuse4","cornflowerblue")) +
  scale_y_log10 () + 
  geom_smooth(aes(color = Coniferous), method = "gam", se = FALSE) +
  facet_wrap(~ Variable, scales = "free", labeller = label_parsed) +
  theme_bw() +
  xlab(NULL) 

ggsave("Figures/Ions_lc.pdf", Plot4, width = 8, height = 3.75, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Ions_lc.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Ions_lc.jpeg")


#Nutrients
Nutrients <- Water_Chem_Climate %>% 
  dplyr::select(c(site_id, Date, coniferous_forest, TotP_ug_L, TotN_ug_L, PO4_ug_L, NO3_ug_L, SiO2_mg_L)) %>% 
  pivot_longer(cols= -c(site_id, Date, coniferous_forest), names_to = "Variable", values_to = "Measurement") %>% 
  mutate(Coniferous = ifelse(coniferous_forest >20, "Coniferous", "Other")) %>% 
  drop_na(Coniferous)

Nutrients$Variable <- factor(Nutrients$Variable,
                        levels = c("TotP_ug_L", "TotN_ug_L", "PO4_ug_L", "NO3_ug_L", "SiO2_mg_L"),
                        labels = c(bquote('TotP'~ (μg~L^-1)),
                                   bquote('TotN'~ (μg~L^-1)),
                                   bquote('PO'[4]~ (μg~L^-1)),
                                   bquote('NO'[3]~ (μg~L^-1)),
                                   bquote('SiO'[2]~ (mg~L^-1))))
  
Plot5 <- Nutrients %>% 
  ggplot(aes(x = Date, y = Measurement)) + 
  geom_point(size = 0.5, color ="gray75", alpha = 0.4) +
  scale_color_manual(values = c("chartreuse4","cornflowerblue")) +
  scale_y_log10 () + 
  geom_smooth(aes(color = Coniferous), method = "gam", se = FALSE) +
  facet_wrap(~ Variable, scales = "free", labeller = label_parsed) +
  theme_bw() +
  xlab(NULL) 

ggsave("Figures/Nutrients_lc.pdf", Plot5, width = 9, height = 5, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Nutrients_lc.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Nutrients_lc.jpeg")


#Carbon
Carbon <- Water_Chem_Climate %>% 
  dplyr::select(c(site_id, Date, coniferous_forest, DOC_mg_L, TOC_mg_L)) %>% 
  pivot_longer(cols= -c(site_id, Date, coniferous_forest), names_to = "Variable", values_to = "Measurement") %>% 
  mutate(Coniferous = ifelse(coniferous_forest >20, "Coniferous", "Other")) %>% 
  drop_na(Coniferous)
  
Carbon$Variable <- factor(Carbon$Variable, levels = c("DOC_mg_L", "TOC_mg_L"),
                          labels = c(bquote('DOC'~ (mg~L^-1)), 
                                     bquote('TOC'~ (mg~L^-1))))

Plot6 <- Carbon %>% 
  ggplot(aes(x = Date, y = Measurement)) + 
  geom_point(size = 0.5, color ="gray75", alpha = 0.4) +
  scale_color_manual(values = c("chartreuse4","cornflowerblue")) +
  scale_y_log10 () + 
  geom_smooth(aes(color = Coniferous), method = "gam", se = FALSE) +
  facet_wrap(~ Variable, scales = "free", labeller = label_parsed) +
  theme_bw() +
  xlab(NULL) 

ggsave("Figures/Carbon_lc.pdf", Plot6, width = 6, height = 2, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Carbon_lc.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Carbon_lc.jpeg")
```


```{r}
#library(timetk)

#plot_stl_diagnostics(Data, .date_var = Date, .value = Temp_C)

# Temp
#plot_seasonal_diagnostics(Data, .date_var = Date, .value = Temp_C, .feature_set= c("month.lbl","quarter", "year"), .y_lab = "Temperature (C)", .geom_outlier_color = "red")

# DOC
#plot_seasonal_diagnostics(Data, .date_var = Date, .value = DOC_mg_L, .feature_set= c("month.lbl","quarter", "year"), .y_lab = "DOC (mg/L)", .geom_outlier_color = "red")
```



```{r}
Water_Chem_Climate <- read_csv("Clean_Data/Water_Chem_Climate.csv")

# Hydrology
Tog_Plotter <- Water_Chem_Climate %>% 
  dplyr::select(c(site_id, Date, gwb_q,mean_elevation, DOC_mg_L, TOC_mg_L)) %>% 
  pivot_longer(cols= -c(site_id, Date, gwb_q, mean_elevation), names_to = "Variable", values_to = "Measurement") 
  

Plot7 <- Tog_Plotter %>% 
  ggplot() + 
  #geom_point(aes(x = Date, y = gwb_q), size = 0.2, color = "gray45") +
  geom_point(aes(x = Date, y = Measurement, color = mean_elevation), size = 1.0) +
  scale_y_continuous(name = "Measurement", # Features of the first axis
  sec.axis = sec_axis(~., name="Discharge")) +  # Add a second axis and specify its features 
  geom_smooth(aes(x = Date, y = gwb_q), method = "gam", se = T, color = "gray45") +
  geom_smooth(aes(x = Date, y = Measurement), method = "gam", se = T, color = "blue") +
  facet_wrap(~ Variable, scales = "free", labeller = label_parsed, ncol=1) +
  theme_bw() +
  xlab(NULL) 

ggsave("Figures/Carbon_discharge.pdf", Plot7, width = 6, height = 6, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Carbon_discharge.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Carbon_discharge.jpeg")
```





# 2018 vs 2020 comparison

```{r}
Water_Chem_Climate <- read_csv("Clean_Data/Water_Chem_Climate.csv")

# Ca
Data <- Water_Chem_Climate %>% 
  mutate(year = year(Date)) %>% 
  mutate(month = month(Date)) %>% 
  mutate(day = day(Date)) %>% 
  mutate(Date = make_date(month, day)) %>% 
  filter(year %in% c("2018", "2020")) %>% 
  dplyr::select(c(site_id, gwb_sssrel, Date, year, SO4_mg_L)) 


Plot <- Data %>% 
  ggplot() + 
 # geom_point(aes(x = Date, y = gwb_sssrel), size = 0.2, color = "gray45") +
  geom_point(aes(x = Date, y = SO4_mg_L), size = 1.0, color = "blue") +
  #scale_y_continuous(name = "Ca_mg_L", # Features of the first axis
 # sec.axis = sec_axis(~., name="gwb-sssrel (%)")) +  # Add a second axis and specify its features 
  #geom_smooth(aes(x = Date, y = gwb_sssrel), method = "gam", se = T, color = "gray45") +
  geom_smooth(aes(x = Date, y = SO4_mg_L), method = "gam", se = T, color = "blue") +
  facet_wrap(~ year, labeller = label_parsed, ncol=1) +
  theme_bw() +
  xlab(NULL) 


Plot <- Data %>% 
  ggplot() + 
  geom_point(aes(x = Date, y = SO4_mg_L), size = 1.0, color = "blue") +
  geom_smooth(aes(x = Date, y = SO4_mg_L), method = "gam", se = T, color = "blue") +
  scale_y_log10 () + 
  facet_wrap(~ year, labeller = label_parsed, ncol=1) +
  theme_bw() +
  xlab(NULL)

ggsave("Figures/Ca.pdf", Plot, width = 6, height = 6, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Ca.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Ca.jpeg")
```


# Waterchem select; by Ecoregion (currently what is in the report)
## Brownification
```{r}
Water_Chem_select <- read_csv("Clean_Data/Water_Chem_select.csv")

# 2018/2020
Wsel <- Water_Chem_select %>% 
  mutate(year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'18/'20")) %>% 
  filter(year %in% c("2018", "2020")) %>% 
  dplyr::select(c(site_id, year, month, okoregion, group, Water_Color_mgPt_l, Fe_ug_L, DOC_mg_L)) %>% 
  pivot_longer(cols= -c(site_id, year, month, group, okoregion), names_to = "Variable", values_to = "Measurement") %>% drop_na()

Wsel$Variable <- factor(Wsel$Variable,
                        levels = c("DOC_mg_L", "Fe_ug_L", "Water_Color_mgPt_l"), 
                        labels = c(bquote('DOC'~ (mg~L^-1)), 
                                   bquote('Fe'~ (μg~L^-1)), 
                                   bquote('Water Color'~ (mgPt~L^-1))))

Plot1 <- Wsel %>% 
  filter(!okoregion %in% c("Midt-Norge", "Sorlandet")) %>% 
  ggplot(aes(x = month, y = Measurement, group = factor(year))) + 
  geom_point(size = 0.5, color ="gray70", alpha = 0.4) +
  scale_color_manual(values=c("#FFCC66", "#264EFF")) +
  scale_y_log10 () + 
  geom_smooth(aes(color = factor(year)), method = "gam", se = FALSE) +
  facet_grid(Variable~okoregion, scales = "free", labeller = label_parsed) +
  theme_bw() +
  xlab(NULL) +
  labs(color ="year") +
  theme(axis.text.x = element_text(size =6, angle = 45, hjust = 1)) 

ggsave("Figures/Wsel_18_20_br.pdf", Plot1, width = 6, height = 5, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Wsel_18_20_br.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Wsel_18_20_br.jpeg")

# 2019/2021

Wsel <- Water_Chem_select %>% 
  mutate(year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'19/'21")) %>% 
  filter(year %in% c("2019", "2021")) %>% 
  dplyr::select(c(site_id, year, month, okoregion, group, Water_Color_mgPt_l, Fe_ug_L, DOC_mg_L)) %>% 
  pivot_longer(cols= -c(site_id, year, month, group, okoregion), names_to = "Variable", values_to = "Measurement") %>% drop_na()

Wsel$Variable <- factor(Wsel$Variable,
                        levels = c("DOC_mg_L", "Fe_ug_L", "Water_Color_mgPt_l"), 
                        labels = c(bquote('DOC'~ (mg~L^-1)), 
                                   bquote('Fe'~ (μg~L^-1)), 
                                   bquote('Water Color'~ (mgPt~L^-1))))

Wsel$okoregion <- factor(Wsel$okoregion,
                        levels = c("Midt-Norge", "Nord-Norge ytre", "Vest", "Sorlandet"),
                        labels = c(bquote('Midt-Norge'),
                                   bquote("Nord-Norge"),
                                   bquote("Vest"),
                                   bquote("Sorlandet")))

Plot2 <- Wsel %>% 
  ggplot(aes(x = month, y = Measurement, group = factor(year))) + 
  geom_point(size = 0.5, color ="gray70", alpha = 0.4) +
  scale_color_manual(values=c("#3399FF", "#FF8000")) +
  scale_y_log10 () + 
  geom_smooth(aes(color = factor(year)), method = "gam", se = FALSE) +
  facet_grid(Variable~okoregion, scales = "free", labeller = label_parsed) +
  theme_bw() +
  xlab(NULL) +
  labs(color ="year") +
  theme(axis.text.x = element_text(size =6, angle = 45, hjust = 1)) 

ggsave("Figures/Wsel_19_21_br.pdf", Plot2, width = 7, height = 5, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Wsel_19_21_br.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Wsel_19_21_br.jpeg")


# Wsel: 2018/2019/2020/2021

Wsel <- Water_Chem_select %>% 
  mutate(year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'18/'19/'20/'21")) %>% 
  filter(year %in% c("2018", "2019", "2020", "2021")) %>% 
 dplyr::select(c(site_id, year, month, okoregion, group, Water_Color_mgPt_l, Fe_ug_L, DOC_mg_L)) %>% 
  pivot_longer(cols= -c(site_id, year, month, group, okoregion), names_to = "Variable", values_to = "Measurement") %>% drop_na()

Wsel$Variable <- factor(Wsel$Variable,
                        levels = c("DOC_mg_L", "Fe_ug_L", "Water_Color_mgPt_l"), 
                        labels = c(bquote('DOC'~ (mg~L^-1)), 
                                   bquote('Fe'~ (μg~L^-1)), 
                                   bquote('Water Color'~ (mgPt~L^-1))))

Plot3 <- Wsel %>% 
  ggplot(aes(x = month, y = Measurement, group = factor(year))) + 
  geom_point(size = 0.5, color ="gray70", alpha = 0.4) +
  scale_color_manual(values=c("#FFCC66","#3399FF","#264EFF", "#FF8000")) +
  scale_y_log10 () + 
  geom_smooth(aes(color = factor(year)), method = "gam", se = FALSE) +
  facet_wrap(~Variable, scales = "free", labeller = label_parsed) +
  theme_bw() +
  xlab(NULL) +
  labs(color ="year") +
  theme(axis.text.x = element_text(size =6, angle = 45, hjust = 1)) 

ggsave("Figures/Wsel_ALL_br.pdf", Plot3, width = 6.5, height = 2, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Wsel_ALL_br.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Wsel_ALL_br.jpeg")
```



## Acidification
```{r}
Water_Chem_select <- read_csv("Clean_Data/Water_Chem_select.csv")

# 2018/2020
Wsel <- Water_Chem_select %>% 
  mutate(year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'18/'20")) %>% 
  filter(year %in% c("2018", "2020")) %>% 
  dplyr::select(c(site_id, year, month, okoregion, group, Temp_C, pH, ANC_µEkv_L, Ca_mg_L)) %>% 
  pivot_longer(cols= -c(site_id, year, month, group, okoregion), names_to = "Variable", values_to = "Measurement") %>% drop_na()


Wsel$Variable <- factor(Wsel$Variable,
                        levels = c("Temp_C","pH", "ANC_µEkv_L", "Ca_mg_L"), 
                        labels = c(bquote('Temp'~ (C)),
                                   bquote('pH'),
                                   bquote('ANC'~ (µEkv~L^-1)),
                                   bquote('Ca'~ (mg~L^-1))))

Plot1 <- Wsel %>% 
  filter(!okoregion %in% c("Midt-Norge", "Sorlandet")) %>% 
  ggplot(aes(x = month, y = Measurement, group = factor(year))) + 
  geom_point(size = 0.5, color ="gray70", alpha = 0.4) +
  scale_color_manual(values=c("#FFCC66", "#264EFF")) +
  scale_y_log10 () + 
  geom_smooth(aes(color = factor(year)), method = "gam", se = FALSE) +
  facet_grid(Variable~okoregion, scales = "free", labeller = label_parsed) +
  theme_bw() +
  xlab(NULL) +
  labs(color ="year") +
  theme(axis.text.x = element_text(size = 6, angle = 45, hjust = 1)) 

ggsave("Figures/Wsel_18_20.pdf", Plot1, width = 7, height = 5, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Wsel_18_20.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Wsel_18_20.jpeg")


# 2019/2021

Wsel <- Water_Chem_select %>% 
  mutate(year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'19/'21")) %>% 
  filter(year %in% c("2019", "2021")) %>% 
  dplyr::select(c(site_id, year, month, okoregion, group, Temp_C, pH, ANC_µEkv_L, Ca_mg_L)) %>% 
  pivot_longer(cols= -c(site_id, year, month, group, okoregion), names_to = "Variable", values_to = "Measurement") %>% drop_na()


Wsel$Variable <- factor(Wsel$Variable,
                        levels = c("Temp_C","pH", "ANC_µEkv_L", "Ca_mg_L"), 
                        labels = c(bquote('Temp'~ (C)),
                                   bquote('pH'),
                                   bquote('ANC'~ (µEkv~L^-1)),
                                   bquote('Ca'~ (mg~L^-1))))

Wsel$okoregion <- factor(Wsel$okoregion,
                        levels = c("Midt-Norge", "Nord-Norge ytre", "Vest", "Sorlandet"),
                        labels = c(bquote('Midt-Norge'),
                                   bquote("Nord-Norge"),
                                   bquote("Vest"),
                                   bquote("Sorlandet")))

Plot2 <- Wsel %>% 
  ggplot(aes(x = month, y = Measurement, group = factor(year))) + 
  geom_point(size = 0.5, color ="gray70", alpha = 0.4) +
  scale_color_manual(values=c("#3399FF", "#FF8000")) +
  scale_y_log10 () + 
  geom_smooth(aes(color = factor(year)), method = "gam", se = FALSE) +
  facet_grid(Variable~okoregion, scales = "free", labeller = label_parsed) +
  theme_bw() +
  xlab(NULL) +
  labs(color ="year") +
  theme(axis.text.x = element_text(size =6, angle = 45, hjust = 1)) 

ggsave("Figures/Wsel_19_21.pdf", Plot2, width = 7, height = 5, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Wsel_19_21.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Wsel_19_21.jpeg")


# Wsel: 2018/2019/2020/2021

Wsel <- Water_Chem_select %>% 
  mutate(year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'18/'19/'20/'21")) %>% 
  filter(year %in% c("2018", "2019", "2020", "2021")) %>% 
  dplyr::select(c(site_id, year, month, okoregion, group, Temp_C, pH, ANC_µEkv_L, Ca_mg_L)) %>% 
  pivot_longer(cols= -c(site_id, year, month, group, okoregion), names_to = "Variable", values_to = "Measurement") %>% drop_na()


Wsel$Variable <- factor(Wsel$Variable,
                        levels = c("Temp_C","pH", "ANC_µEkv_L", "Ca_mg_L"), 
                        labels = c(bquote('Temp'~ (C)),
                                   bquote('pH'),
                                   bquote('ANC'~ (µEkv~L^-1)),
                                   bquote('Ca'~ (mg~L^-1))))

Plot3 <- Wsel %>% 
  ggplot(aes(x = month, y = Measurement, group = factor(year))) + 
  geom_point(size = 0.5, color ="gray70", alpha = 0.4) +
  scale_color_manual(values=c("#FFCC66","#3399FF","#264EFF", "#FF8000")) +
  scale_y_log10 () + 
  geom_smooth(aes(color = factor(year)), method = "gam", se = FALSE) +
  facet_wrap(~Variable, scales = "free", labeller = label_parsed) +
  theme_bw() +
  xlab(NULL) +
  labs(color ="year") +
  theme(axis.text.x = element_text(size =8, angle = 45, hjust = 1)) 

ggsave("Figures/Wsel_ALL_acid.pdf", Plot3, width = 5.5, height = 3, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Wsel_ALL_acid.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Wsel_ALL_acid.jpeg")
```



## Nutrification

```{r}
Water_Chem_select <- read_csv("Clean_Data/Water_Chem_select.csv")

# 2018/2020
Wsel <- Water_Chem_select %>% 
  mutate(year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'18/'20")) %>% 
  filter(year %in% c("2018", "2020")) %>% 
  dplyr::select(c(site_id, year, month, okoregion, group, TotP_ug_L, TotN_ug_L, NO3_ug_L)) %>% 
  group_by(site_id, year, month) %>% 
  mutate(TN_TP = TotN_ug_L/TotP_ug_L, DIN_TP =NO3_ug_L/TotP_ug_L) %>% ungroup() %>% 
  pivot_longer(cols= -c(site_id, year, month, group, okoregion), names_to = "Variable", values_to = "Measurement") %>% drop_na()


Wsel$Variable <- factor(Wsel$Variable,
                        levels = c("TotP_ug_L", "TotN_ug_L", "NO3_ug_L", "TN_TP", "DIN_TP"), 
                        labels = c(bquote('TotP'~ (μg~L^-1)),
                                   bquote('TotN'~ (μg~L^-1)), 
                                   bquote('NO'[3]~ (μg~L^-1)),
                                   "TN:TP", "NO3:TP"))

Plot1 <- Wsel %>% 
  filter(!okoregion %in% c("Midt-Norge", "Sorlandet")) %>% 
  ggplot(aes(x = month, y = Measurement, group = factor(year))) + 
  geom_point(size = 0.5, color ="gray70", alpha = 0.4) +
  scale_color_manual(values=c("#FFCC66", "#264EFF")) +
  scale_y_log10 () + 
  geom_smooth(aes(color = factor(year)), method = "gam", se = FALSE) +
  facet_grid(Variable~okoregion, scales = "free", labeller = label_parsed) +
  theme_bw() +
  xlab(NULL) +
  labs(color ="year") +
  theme(axis.text.x = element_text(size =6, angle = 45, hjust = 1)) 

ggsave("Figures/Wsel_18_20_Nut.pdf", Plot1, width = 6, height = 6, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Wsel_18_20_Nut.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Wsel_18_20_Nut.jpeg")


# 2019/2021

Wsel <- Water_Chem_select %>% 
  mutate(year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'19/'21")) %>% 
  filter(year %in% c("2019", "2021")) %>% 
 dplyr::select(c(site_id, year, month, okoregion, group, TotP_ug_L, TotN_ug_L, NO3_ug_L)) %>% 
  group_by(site_id, year, month) %>% 
  mutate(TN_TP = TotN_ug_L/TotP_ug_L, DIN_TP =NO3_ug_L/TotP_ug_L) %>% ungroup() %>% 
  pivot_longer(cols= -c(site_id, year, month, group, okoregion), names_to = "Variable", values_to = "Measurement") %>% drop_na()

Wsel$Variable <- factor(Wsel$Variable,
                        levels = c("TotP_ug_L", "TotN_ug_L", "NO3_ug_L", "TN_TP", "DIN_TP"), 
                        labels = c(bquote('TotP'~ (μg~L^-1)),
                                   bquote('TotN'~ (μg~L^-1)), 
                                   bquote('NO'[3]~ (μg~L^-1)),
                                   "TN:TP", "NO3:TP"))

Wsel$okoregion <- factor(Wsel$okoregion,
                        levels = c("Midt-Norge", "Nord-Norge ytre", "Vest", "Sorlandet"),
                        labels = c(bquote('Midt-Norge'),
                                   bquote("Nord-Norge"),
                                   bquote("Vest"),
                                   bquote("Sorlandet")))

Plot2 <- Wsel %>% 
  ggplot(aes(x = month, y = Measurement, group = factor(year))) + 
  geom_point(size = 0.5, color ="gray70", alpha = 0.4) +
  scale_color_manual(values=c("#3399FF", "#FF8000")) +
  scale_y_log10 () + 
  geom_smooth(aes(color = factor(year)), method = "gam", se = FALSE) +
  facet_grid(Variable~okoregion, scales = "free", labeller = label_parsed) +
  theme_bw() +
  xlab(NULL) +
  labs(color ="year") +
  theme(axis.text.x = element_text(size =6, angle = 45, hjust = 1)) 

ggsave("Figures/Wsel_19_21_Nut.pdf", Plot2, width = 7, height = 6, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Wsel_19_21_Nut.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Wsel_19_21_Nut.jpeg")


# Wsel: 2018/2019/2020/2021

Wsel <- Water_Chem_select %>% 
  mutate(year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'18/'19/'20/'21")) %>% 
  filter(year %in% c("2018", "2019", "2020", "2021")) %>% 
  dplyr::select(c(site_id, year, month, okoregion, group, TotP_ug_L, TotN_ug_L, NO3_ug_L)) %>% 
  group_by(site_id, year, month) %>% 
  mutate(TN_TP = TotN_ug_L/TotP_ug_L, DIN_TP =NO3_ug_L/TotP_ug_L) %>% ungroup() %>% 
  pivot_longer(cols= -c(site_id, year, month, group, okoregion), names_to = "Variable", values_to = "Measurement") %>%  
  drop_na()


Wsel$Variable <- factor(Wsel$Variable,
                        levels = c("TotP_ug_L", "TotN_ug_L", "NO3_ug_L", "TN_TP", "DIN_TP"), 
                        labels = c(bquote('TotP'~ (μg~L^-1)),
                                   bquote('TotN'~ (μg~L^-1)), 
                                   bquote('NO'[3]~ (μg~L^-1)),
                                   "TN:TP", "NO3:TP"))

Plot3 <- Wsel %>% 
  ggplot(aes(x = month, y = Measurement, group = factor(year))) + 
  geom_point(size = 0.5, color ="gray70", alpha = 0.4) +
  scale_color_manual(values=c("#FFCC66","#3399FF","#264EFF", "#FF8000")) +
  scale_y_log10 () + 
  geom_smooth(aes(color = factor(year)), method = "gam", se = FALSE) +
  facet_wrap(~Variable, scales = "free", labeller = label_parsed) +
  theme_bw() +
  xlab(NULL) +
  labs(color ="year") +
  theme(axis.text.x = element_text(size =8, angle = 45, hjust = 1)) 

ggsave("Figures/Wsel_ALL_Nut.pdf", Plot3, width = 7.3, height = 3.5, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/Wsel_ALL_Nut.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/Wsel_ALL_Nut.jpeg")
```


# Log Ratios 2018/2021
```{r}
library("RColorBrewer")
library(scales)
Water_Chem_select <- read_csv("Clean_Data/Water_Chem_select.csv") 
X <- read_csv("Clean_Data/Intermediate/Drought_Data_daily.csv") %>% 
  filter(par == "gwb_sssrel") %>% 
  filter(year == "2018") %>% 
  mutate(soil_moisture = value_mean) %>% 
  dplyr::select(c(site_id, soil_moisture, month)) %>% 
  group_by(site_id, month) %>% 
  summarise(soil_moisture =  mean(soil_moisture))

# Doubles need to be removed before ratios between 2018 and 2020 can be calculated
# F_238_48_San & O_002_2053_Sto #set/oct  change 2018-09-30 to 2018-10-01
# O_015_687_Sma & O_015_920_Num #jun/july change 2020-06-30 to 2020-07-01
# F_234_229_Mas #oct/nov change 2018-10-30 to 2018-11-01

Water_Chem2_2018 <- full_join(Water_Chem_select, X) %>%
    filter(okoregion %in% c("Finnmark", "Ostlandet", "Vest")) %>% 
     mutate(Date = ifelse(grepl("F_238_48_San|O_002_2053_Sto", site_id) & Date == "2018-09-30", as_date("2018-10-01"), as_date(Date)),
         Date = as_date(Date), 
         Date = ifelse(grepl("O_015_687_Sma|O_015_920_Num", site_id) & Date == "2020-06-30", as_date("2020-07-01"), as_date(Date)), 
         Date = as_date(Date), 
         Date = ifelse(grepl("F_234_229_Mas", site_id) & Date == "2018-10-30", as_date("2018-11-01"), as_date(Date)), 
         Date = as_date(Date), 
         Date = ymd(Date), year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'18/'20")) %>% 
  filter(year %in% c("2018", "2020")) %>% 
  filter(!(site_id == "O_002_300_Atn_DAN03" & month == "Oct"  & year == "2018"))


TP_Ratio <- Water_Chem2_2018 %>% 
  distinct() %>% drop_na(TotP_ug_L) %>% 
  dplyr::select(c(site_id, year, month, okoregion, TotP_ug_L,  soil_moisture)) %>% 
  pivot_wider(names_from = year, values_from = TotP_ug_L) %>% 
  group_by(site_id, month) %>% 
  mutate(TP = log10(`2018`/`2020`)) %>% 
  dplyr::select(c(site_id, month,okoregion,TP,  soil_moisture)) %>% 
  mutate(hypothesis = "nuts")
           
TN_Ratio <- Water_Chem2_2018 %>% 
  distinct() %>% drop_na(TotN_ug_L) %>% 
  dplyr::select(c(site_id, year, month, okoregion, TotN_ug_L,  soil_moisture)) %>% 
  pivot_wider(names_from = year, values_from = TotN_ug_L) %>% 
  group_by(site_id, month) %>% 
  mutate(TN = log10(`2018`/`2020`)) %>% 
  dplyr::select(site_id, month, okoregion, TN,  soil_moisture) %>% 
  mutate(hypothesis = "nuts")

NO3_Ratio <- Water_Chem2_2018 %>% 
  distinct() %>% drop_na(NO3_ug_L) %>% 
  dplyr::select(c(site_id, year, month, okoregion, NO3_ug_L,  soil_moisture)) %>% 
  pivot_wider(names_from = year, values_from = NO3_ug_L) %>% 
  group_by(site_id, month) %>% 
  mutate(NO3 = log10(`2018`/`2020`)) %>% 
  dplyr::select(site_id, month,okoregion, NO3,  soil_moisture) %>% 
  mutate(hypothesis = "nuts")

NP_RatioP <- Water_Chem2_2018 %>% 
  distinct() %>% drop_na(NO3_ug_L) %>% 
  dplyr::select(c(site_id, year, month, okoregion, NO3_ug_L, TotP_ug_L, soil_moisture)) %>% 
  group_by(site_id, year, month, okoregion) %>% 
  mutate(NP_Ratio = NO3_ug_L/TotP_ug_L) %>% 
  ungroup() %>% 
  dplyr::select(-c(NO3_ug_L, TotP_ug_L)) %>% 
  pivot_wider(names_from = year, values_from = NP_Ratio) %>% 
  group_by(site_id, month) %>% 
  mutate(NP_Ratio = log10(`2018`/`2020`)) %>% ungroup %>% 
  dplyr::select(c(site_id, month,okoregion, NP_Ratio,  soil_moisture)) %>% 
  mutate(hypothesis = "nuts")
           
DOC_Ratio <- Water_Chem2_2018 %>% 
  distinct() %>% drop_na(DOC_mg_L) %>% 
  dplyr::select(c(site_id, year, month, okoregion, DOC_mg_L,  soil_moisture)) %>% 
  pivot_wider(names_from = year, values_from = DOC_mg_L) %>% 
  group_by(site_id, month) %>% 
  mutate(DOC = log10(`2018`/`2020`)) %>% 
  dplyr::select(c(site_id, month,okoregion,DOC, soil_moisture)) %>% 
  mutate(hypothesis = "brown")
           
Color_Ratio <- Water_Chem2_2018 %>% 
  distinct() %>% drop_na(Water_Color_mgPt_l) %>% 
  dplyr::select(c(site_id, year, month, okoregion, Water_Color_mgPt_l, soil_moisture)) %>% 
  pivot_wider(names_from = year, values_from = Water_Color_mgPt_l) %>% 
  group_by(site_id, month) %>% 
  mutate(Color = log10(`2018`/`2020`)) %>% 
  dplyr::select(site_id, month, okoregion, Color, soil_moisture) %>% 
  mutate(hypothesis = "brown")

Fe_Ratio <- Water_Chem2_2018 %>% 
  distinct() %>% drop_na(Fe_ug_L) %>% 
  dplyr::select(c(site_id, year, month, okoregion, Fe_ug_L, soil_moisture)) %>% 
  pivot_wider(names_from = year, values_from = Fe_ug_L) %>% 
  group_by(site_id, month) %>% 
  mutate(Fe = log10(`2018`/`2020`)) %>% 
  dplyr::select(site_id, month,okoregion, Fe, soil_moisture) %>% 
  mutate(hypothesis = "brown")

Temp_Ratio <- Water_Chem2_2018 %>% 
  distinct() %>% drop_na(Temp_C) %>% 
  dplyr::select(c(site_id, year, month, okoregion, Temp_C, soil_moisture)) %>% 
  pivot_wider(names_from = year, values_from = Temp_C) %>% 
  group_by(site_id, month) %>% 
  mutate(Temp = log10(`2018`/`2020`)) %>% 
  dplyr::select(c(site_id, month,okoregion,Temp, soil_moisture)) %>% 
  mutate(hypothesis = "brown")
           
Ca_Ratio <- Water_Chem2_2018 %>% 
  distinct() %>% drop_na(Ca_mg_L) %>% 
  dplyr::select(c(site_id, year, month, okoregion, Ca_mg_L, soil_moisture)) %>% 
  pivot_wider(names_from = year, values_from = Ca_mg_L) %>% 
  group_by(site_id, month) %>% 
  mutate(Ca = log10(`2018`/`2020`)) %>% 
  dplyr::select(site_id, month, okoregion, Ca, soil_moisture) %>% 
  mutate(hypothesis = "acid")

pH_Ratio <- Water_Chem2_2018 %>% 
  distinct() %>% drop_na(pH) %>% 
  dplyr::select(c(site_id, year, month, okoregion, pH, soil_moisture)) %>% 
  pivot_wider(names_from = year, values_from = pH) %>% 
  group_by(site_id, month) %>% 
  mutate(pH = log10(`2018`/`2020`)) %>% 
  dplyr::select(site_id, month, okoregion, pH, soil_moisture) %>% 
  mutate(hypothesis = "acid")

SO4_Ratio <- Water_Chem2_2018 %>% 
  distinct() %>% drop_na(SO4_mg_L) %>% 
  dplyr::select(c(site_id, year, month, okoregion, SO4_mg_L, soil_moisture)) %>% 
  pivot_wider(names_from = year, values_from = SO4_mg_L) %>% 
  group_by(site_id, month) %>% 
  mutate(SO4 = log10(`2018`/`2020`)) %>% 
  dplyr::select(site_id, month, okoregion, SO4, soil_moisture) %>% 
  mutate(hypothesis = "acid")

ANC_Ratio <- Water_Chem2_2018 %>% 
  distinct() %>% drop_na(ANC_µEkv_L) %>% 
  dplyr::select(c(site_id, year, month, okoregion, ANC_µEkv_L, soil_moisture)) %>% 
  pivot_wider(names_from = year, values_from = ANC_µEkv_L) %>% 
  group_by(site_id, month) %>% 
  mutate(ANC = log(`2018`/`2020`)) %>% 
  dplyr::select(site_id, month,okoregion, ANC, soil_moisture) %>% 
  mutate(hypothesis = "acid")
           
X <- full_join(Temp_Ratio, Ca_Ratio)
XX <- full_join(pH_Ratio, SO4_Ratio)
XX2 <- full_join(X,XX)
Y <- full_join(DOC_Ratio, Color_Ratio)
YY <- full_join(Y, Fe_Ratio) 
YY2 <- full_join(Y,YY)
Z <- full_join(TP_Ratio, TN_Ratio)
ZZ <- full_join(NP_RatioP, NO3_Ratio) 
ZZ2 <- full_join(Z, ZZ) 
XY<- full_join(XX2, YY2) 

data <-  full_join(XY, ZZ2) %>% 
  pivot_longer(cols= c(TP, TN, NO3, NP_Ratio, Temp, Ca, SO4, pH, DOC, Color, Fe), names_to = "variable", values_to = "logratio_18_20") %>% 
  drop_na() 

# T-tests
library(broom)
library(caret)
library(glue)

my.t.test.p.value <- function(...) {
    obj<-try(t.test(...), silent=TRUE)
    if (is(obj, "try-error")) return(NA) else return(obj$p.value)
 }

T_testR <- data %>%
  dplyr::select(site_id, okoregion, month, variable, logratio_18_20, hypothesis) %>% 
  ungroup() %>% distinct() %>% dplyr::select(-site_id) %>% 
  unite("ID", okoregion, month, variable, hypothesis, sep = "-", remove = TRUE) %>% 
  nest(data = -c(ID)) %>%  
  mutate(t_test = map(data, ~my.t.test.p.value(.x$logratio_18_20))) %>% 
  dplyr::select(-c(data)) %>% 
  unnest(t_test) %>% 
  mutate(p_value = round(t_test, 4)) %>% 
  dplyr::select(c(ID, p_value)) %>% 
  filter(p_value < 0.05) %>% 
  mutate(sign = "*") %>% 
  separate(ID, c("okoregion", "month", "variable", "hypothesis"), sep = "-")

# Plot

data$variable <- factor(data$variable,
                       levels = c("Temp", "pH", "Ca", "SO4", "DOC", "Color", "Fe", "NO3", "TN", "TP", "NP_Ratio"),
                       labels = c("Temp", "pH", "Ca",  bquote('SO'[4]), "DOC", "Color", "Fe",
                                  bquote('NO'[3]),
                                  bquote("TotN"), 
                                  bquote("TotP"), 
                                  bquote('NO'[3]~':TotP')))

T_testR$variable <- factor(T_testR$variable,
                       levels = c("Temp", "pH", "Ca", "SO4", "DOC", "Color", "Fe", "NO3", "TN", "TP", "NP_Ratio"),
                       labels = c("Temp", "pH", "Ca",  bquote('SO'[4]), "DOC", "Color", "Fe",
                                  bquote('NO'[3]),
                                  bquote("TotN"), 
                                  bquote("TotP"), 
                                  bquote('NO'[3]~':TotP')))

T_testR$okoregion <- factor(T_testR$okoregion,
                            levels = c("Finnmark", "Ostlandet", "Vest"),
                            labels = c("Finnmark", "Østlandet", "Vestlandet"))

data$okoregion <- factor(data$okoregion,
                            levels = c("Finnmark", "Ostlandet", "Vest"),
                            labels = c("Finnmark", "Østlandet", "Vestlandet"))

# brown
Plot1 <- ggplot() +
  geom_point(data = (data %>% filter(hypothesis == "brown")), aes(y = logratio_18_20, x = month, color = soil_moisture/100)) +
  geom_hline(yintercept=0, linetype="dashed", color = "black", size=0.5) +
  facet_grid(variable~okoregion, labeller = label_parsed) +
  scale_colour_gradient2(low = "red", mid = "red", high = "white", labels = percent) +
  theme_bw() +
  ylab(bquote('log'[10]~"(2018:2020)")) + xlab(NULL) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
  geom_text(data = (T_testR %>% filter(hypothesis == "brown")), aes(y = 0.7, x = month, label = sign), size = 6, color = "black") +
  labs(color = "soil moisture")

ggsave("Figures/logratio_18_20_brown.pdf", Plot1, width = 8, height = 5, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/logratio_18_20_brown.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/logratio_18_20_brown.jpeg")


# Nuts
Plot2 <- ggplot() +
  geom_point(data = (data %>% filter(hypothesis == "nuts")), aes(y = logratio_18_20, x = month, color = soil_moisture/100)) +
  geom_hline(yintercept=0, linetype="dashed", color = "black", size=0.5) +
  facet_grid(variable~okoregion, labeller = label_parsed) +
  scale_colour_gradient2(low = "red", mid = "red", high = "white", labels = percent) +
  theme_bw() +
  ylab(bquote('log'[10]~"(2018:2020)")) + xlab(NULL) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
  geom_text(data = (T_testR %>% filter(hypothesis == "nuts")), aes(y = 0.7, x = month, label = sign), size = 6, color = "black") +
  labs(color = "soil moisture")

ggsave("Figures/logratio_18_20_nuts.pdf", Plot2, width = 8, height = 5, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/logratio_18_20_nuts.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/logratio_18_20_nuts.jpeg")

# acid
Plot3 <- ggplot() +
  geom_point(data = (data %>% filter(hypothesis == "acid")), aes(y = logratio_18_20, x = month, color = soil_moisture/100)) +
  geom_hline(yintercept=0, linetype="dashed", color = "black", size=0.5) +
  facet_grid(variable~okoregion, labeller = label_parsed, scales = "free") +
  scale_colour_gradient2(low = "red", mid = "red", high = "white", labels = percent) +
  theme_bw() +
  ylab(bquote('log'[10]~"(2018:2020)")) + xlab(NULL) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
  geom_text(data = (T_testR %>% filter(hypothesis == "acid")), aes(y = 0.7, x = month, label = sign), size = 6, color = "black") +
  labs(color = "soil moisture")

ggsave("Figures/logratio_18_20_acid.pdf", Plot3, width = 8, height = 4, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/logratio_18_20_acid.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/logratio_18_20_acid.jpeg")
```



# Log Ratios 2019/2021
```{r}
library("RColorBrewer")
Water_Chem_select <- read_csv("Clean_Data/Water_Chem_select.csv") %>% 
  mutate(month= month(Date, label = T))
X <- read_csv("Clean_Data/Intermediate/Drought_Data_daily.csv") %>% 
  filter(par == "gwb_sssrel") %>% 
  filter(year == "2021") %>% 
  mutate(soil_moisture = value_mean) %>% 
  dplyr::select(c(site_id, soil_moisture, month)) %>% 
  group_by(site_id, month) %>% 
  summarise(soil_moisture =  mean(soil_moisture))

# Doubles need to be removed before ratios between 2019 and 2021 can be calculated
# M_120_27_Sto  Feb   2021   	2021-02-28 to 2021-03-01
# S_017_17_Ror   Feb  2021    2021-02-28 to 2021-03-01
# M_120_27_Sto  June  2021    2021-06-29  to 2021-07-01
# M_123_499_Hom  June 2021    2021-06-30  to 2021-07-01
# V_027_139_Hal  Aug  2021    2021-08-31  to 2021-09-01
# M_120_27_Sto  Nov   2021    2021-09-28  to 2021-10-01
# M_120_27_Sto  Sept  2021    2021-11-30  to 2021-12-01
# M_105_36_Bre  Feb   2019    2019-02-27 to 2019-03-01
# S_021_1042_Lis Mar  2019    2019-03-27 to 2019-04-01
# S_021_1187_Ves Mar  2019....2019-03-27 to 2019-04-01
# M_139_219_San Apr   2019    2019-04-30 to 2019-05-01
# M_139_50_Lur   Apr  2019    2019-04-30 to 2019-05-01
# N_195_59_Fla  Jul   2019  	2019-07-29 to 2019-08-01
# S_025_327_San   Jul 2019    2019-07-30 to 2019-08-01
# S_026_640_Mol   JUl 2019  	2019-07-30 to 2019-08-01

Water_Chem2_2019 <- full_join(Water_Chem_select, X) %>%
  mutate(year = year(Date)) %>% distinct() %>% 
  filter(group %in% c("'19/'21")) %>% 
  filter(year %in% c("2019", "2021")) %>% 
  mutate(Date = ifelse(grepl("M_120_27_Sto|S_017_17_Ror", site_id) & Date == "2021-02-28", as_date("2021-03-01"), as_date(Date)), Date = as_date(Date), 
  Date = ifelse(grepl("M_120_27_Sto", site_id) & Date == "2021-06-29", as_date("2021-07-01"), as_date(Date)),Date = as_date(Date), 
  Date = ifelse(site_id == "M_123_499_Hom" & Date == "2021-06-30", as_date("2021-07-01"), as_date(Date)), Date = as_date(Date),
  Date = ifelse(site_id == "V_027_139_Hal" & Date == "2021-08-31", as_date("2021-09-01"), as_date(Date)), Date = as_date(Date),
  Date = ifelse(site_id == "M_120_27_Sto" & Date == "2021-09-28", as_date("2021-10-01"), as_date(Date)), Date = as_date(Date),
  Date = ifelse(site_id == "M_120_27_Sto" & Date == "2021-11-30", as_date("2021-12-01"), as_date(Date)), Date = as_date(Date),
  Date = ifelse(site_id == "M_105_36_Bre" & Date == "2019-02-27", as_date("2019-03-01"), as_date(Date)), Date = as_date(Date),
  Date = ifelse(grepl("S_021_1042_Lis|S_021_1187_Ves", site_id) & Date == "2019-03-27", as_date("2019-04-01"), as_date(Date)), Date = as_date(Date),
  Date = ifelse(grepl("M_139_219_San|M_139_50_Lur", site_id) & Date == "2019-04-30", as_date("2019-05-01"), as_date(Date)), Date = as_date(Date),
  Date = ifelse(site_id == "N_195_59_Fla" & Date == "2019-07-29", as_date("2019-08-01"), as_date(Date)), Date = as_date(Date),
  Date = ifelse(grepl("S_025_327_San|S_026_640_Mol", site_id) & Date == "2019-07-30", as_date("2019-08-01"), as_date(Date)), Date = as_date(Date),
  Date = ymd(Date), year = year(Date), month = month(Date, label = TRUE))


TP_Ratio <- Water_Chem2_2019 %>% 
  distinct() %>% drop_na(TotP_ug_L) %>% 
  dplyr::select(c(site_id, year, month, okoregion, TotP_ug_L,  soil_moisture)) %>% 
  pivot_wider(names_from = year, values_from = TotP_ug_L) %>% 
  group_by(site_id, month) %>% 
  mutate(TP = log10(`2019`/`2021`)) %>% 
  dplyr::select(c(site_id, month,okoregion,TP,  soil_moisture))
           
TN_Ratio <- Water_Chem2_2019 %>% 
  distinct() %>% drop_na(TotN_ug_L) %>% 
  dplyr::select(c(site_id, year, month, okoregion, TotN_ug_L,  soil_moisture)) %>% 
  pivot_wider(names_from = year, values_from = TotN_ug_L) %>% 
  group_by(site_id, month) %>% 
  mutate(TN = log10(`2019`/`2021`)) %>% 
  dplyr::select(site_id, month, okoregion, TN,  soil_moisture)

NO3_Ratio <- Water_Chem2_2019 %>% 
  distinct() %>% drop_na(NO3_ug_L) %>% 
  dplyr::select(c(site_id, year, month, okoregion, NO3_ug_L,  soil_moisture)) %>% 
  pivot_wider(names_from = year, values_from = NO3_ug_L) %>% 
  group_by(site_id, month) %>% 
  mutate(NO3 = log10(`2019`/`2021`)) %>% 
  dplyr::select(site_id, month,okoregion, NO3,  soil_moisture)

NP_RatioP <- Water_Chem2_2019 %>% 
  distinct() %>% drop_na(NO3_ug_L) %>% 
  dplyr::select(c(site_id, year, month, okoregion, NO3_ug_L, TotP_ug_L, soil_moisture)) %>% 
  group_by(site_id, year, month, okoregion) %>% 
  mutate(NP_Ratio = NO3_ug_L/TotP_ug_L) %>% 
  ungroup() %>% 
  dplyr::select(-c(NO3_ug_L, TotP_ug_L)) %>% 
  pivot_wider(names_from = year, values_from = NP_Ratio) %>% 
  group_by(site_id, month) %>% 
  mutate(NP_Ratio = log10(`2019`/`2021`)) %>% ungroup %>% 
  dplyr::select(c(site_id, month,okoregion, NP_Ratio,  soil_moisture))
           
DOC_Ratio <- Water_Chem2_2019 %>% 
  distinct() %>% drop_na(DOC_mg_L) %>% 
  dplyr::select(c(site_id, year, month, okoregion, DOC_mg_L,  soil_moisture)) %>% 
  pivot_wider(names_from = year, values_from = DOC_mg_L) %>% 
  group_by(site_id, month) %>% 
  mutate(DOC = log10(`2019`/`2021`)) %>% 
  dplyr::select(c(site_id, month,okoregion,DOC, soil_moisture))
           
Color_Ratio <- Water_Chem2_2019 %>% 
  distinct() %>% drop_na(Water_Color_mgPt_l) %>% 
  dplyr::select(c(site_id, year, month, okoregion, Water_Color_mgPt_l, soil_moisture)) %>% 
  pivot_wider(names_from = year, values_from = Water_Color_mgPt_l) %>% 
  group_by(site_id, month) %>% 
  mutate(Color = log10(`2019`/`2021`)) %>% 
  dplyr::select(site_id, month, okoregion, Color, soil_moisture)

Fe_Ratio <- Water_Chem2_2019 %>% 
  distinct() %>% drop_na(Fe_ug_L) %>% 
  dplyr::select(c(site_id, year, month, okoregion, Fe_ug_L, soil_moisture)) %>% 
  pivot_wider(names_from = year, values_from = Fe_ug_L) %>% 
  group_by(site_id, month) %>% 
  mutate(Fe = log10(`2019`/`2021`)) %>% 
  dplyr::select(site_id, month,okoregion, Fe, soil_moisture)

Temp_Ratio <- Water_Chem2_2019 %>% 
  distinct() %>% drop_na(Temp_C) %>% 
  dplyr::select(c(site_id, year, month, okoregion, Temp_C, soil_moisture)) %>% 
  pivot_wider(names_from = year, values_from = Temp_C) %>% 
  group_by(site_id, month) %>% 
  mutate(Temp = log10(`2019`/`2021`)) %>% 
  dplyr::select(c(site_id, month,okoregion,Temp, soil_moisture))
           
Ca_Ratio <- Water_Chem2_2019 %>% 
  distinct() %>% drop_na(Ca_mg_L) %>% 
  dplyr::select(c(site_id, year, month, okoregion, Ca_mg_L, soil_moisture)) %>% 
  pivot_wider(names_from = year, values_from = Ca_mg_L) %>% 
  group_by(site_id, month) %>% 
  mutate(Ca = log10(`2019`/`2021`)) %>% 
  dplyr::select(site_id, month, okoregion, Ca, soil_moisture)

pH_Ratio <- Water_Chem2_2019 %>% 
  distinct() %>% drop_na(pH) %>% 
  dplyr::select(c(site_id, year, month, okoregion, pH, soil_moisture)) %>% 
  pivot_wider(names_from = year, values_from = pH) %>% 
  group_by(site_id, month) %>% 
  mutate(pH = log10(`2019`/`2021`)) %>% 
  dplyr::select(site_id, month, okoregion, pH, soil_moisture)

SO4_Ratio <- Water_Chem2_2019 %>% 
  distinct() %>% drop_na(SO4_mg_L) %>% 
  dplyr::select(c(site_id, year, month, okoregion, SO4_mg_L, soil_moisture)) %>% 
  pivot_wider(names_from = year, values_from = SO4_mg_L) %>% 
  group_by(site_id, month) %>% 
  mutate(SO4 = log10(`2019`/`2021`)) %>% 
  dplyr::select(site_id, month, okoregion, SO4, soil_moisture)

ANC_Ratio <- Water_Chem2_2019 %>% 
  distinct() %>% drop_na(ANC_µEkv_L) %>% 
  dplyr::select(c(site_id, year, month, okoregion, ANC_µEkv_L, soil_moisture)) %>% 
  pivot_wider(names_from = year, values_from = ANC_µEkv_L) %>% 
  group_by(site_id, month) %>% 
  mutate(ANC = log10(`2019`/`2021`)) %>% 
  dplyr::select(site_id, month,okoregion, ANC, soil_moisture)
           
X <- full_join(Temp_Ratio, Ca_Ratio)
XX <- full_join(pH_Ratio, SO4_Ratio)
XX2 <- full_join(X,XX)
Y <- full_join(DOC_Ratio, Color_Ratio)
YY <- full_join(Y, Fe_Ratio) 
YY2 <- full_join(Y,YY)
Z <- full_join(TP_Ratio, TN_Ratio)
ZZ <- full_join(NP_RatioP, NO3_Ratio) 
ZZ2 <- full_join(Z, ZZ) 
XY<- full_join(XX2, YY2) 

data <-  full_join(XY, ZZ2) %>% 
  pivot_longer(cols= c(TP, TN, NO3, NP_Ratio, Temp, Ca, SO4, pH, DOC, Color, Fe), names_to = "variable", values_to = "logratio_19_21") %>% 
  drop_na() %>% distinct()

data$variable <- factor(data$variable,
  levels = c("Temp", "pH", "Ca", "SO4", "DOC", "Color", "Fe", "NO3", "TN", "TP", "NP_Ratio"),
  labels = c("Temp", "pH", "Ca", bquote('SO'[4]), "DOC", "Color", "Fe", bquote('NO'[3]), bquote("TotN"), bquote("TotP"), bquote('NO'[3]~':TotP')))

data$okoregion <- factor(data$okoregion,
  levels = c("Midt-Norge", "Nord-Norge ytre", "Sorlandet", "Vest"),
  labels = c("Midt-Norge", "Nord-Norge", "Sorlandet", "Vest"))

# T-tests
library(broom)
library(caret)
library(glue)

my.t.test.p.value <- function(...) {
    obj<-try(t.test(...), silent=TRUE)
    if (is(obj, "try-error")) return(NA) else return(obj$p.value)
 }

T_testR <- data %>%
  dplyr::select(site_id, okoregion, month, variable, logratio_19_21) %>% 
  ungroup() %>% distinct() %>% dplyr::select(-site_id) %>% 
  unite("ID", okoregion, month, variable, sep = "_", remove = TRUE) %>% 
  nest(data = -c(ID)) %>%  
  mutate(t_test = map(data, ~my.t.test.p.value(.x$logratio_19_21))) %>% 
  dplyr::select(-c(data)) %>% 
  unnest(t_test) %>% 
  mutate(p_value = round(t_test, 4)) %>% 
  dplyr::select(c(ID, p_value)) %>% 
  filter(p_value < 0.05) %>% 
  mutate(sign = "*") %>% 
  separate(ID, c("okoregion", "month", "variable"), sep = "_")

# Plot
library(scales)
Plot2 <- ggplot() +
  geom_point(data = data, aes(y = logratio_19_21, x = month, color = soil_moisture/100)) +
  geom_hline(yintercept=0, linetype="dashed", color = "black", size=0.5) +
  facet_grid(variable~okoregion, labeller = label_parsed) +
  scale_colour_gradient2(low = "red", mid = "red", high = "white", labels = percent) +
  theme_bw() +
  ylab(bquote('log'[10]~"(2019:2021)")) + xlab(NULL) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
  geom_text(data = T_testR, aes(y = 0.7, x = month, label = sign), size = 6, color = "black") +
  labs(color = "soil moisture")

ggsave("Figures/logratio_19_21_ALL.pdf", Plot2, width = 10, height = 12, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/logratio_19_21_ALL.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/logratio_19_21_ALL.jpeg")
```




## Nutrients
```{r}
library("RColorBrewer")
Water_Chem_select <- read_csv("Clean_Data/Water_Chem_select.csv") 
X <- read_csv("Clean_Data/Intermediate/Drought_Data_daily.csv") %>% 
  filter(par == "gwb_sssrel") %>% 
  filter(year == "2018") %>% 
#  group_by(okoregion, year) %>% 
  mutate(soil_moisture = value_mean) %>% 
  dplyr::select(c(site_id, soil_moisture, month))

Water_Chem2 <- full_join(Water_Chem_select, X)
# Doubles need to be removed before ratios between 2018 and 2020 can be calculated
# F_238_48_San & O_002_2053_Sto #set/oct  change 2018-09-30 to 2018-10-01
# O_015_687_Sma & O_015_920_Num #jun/july change 2020-06-30 to 2020-07-01
# F_234_229_Mas #oct/nov change 2018-10-30 to 2018-11-01

# TP
TP_Ratio <- Water_Chem2 %>% 
  mutate(Date = ifelse(grepl("F_238_48_San|O_002_2053_Sto", site_id) & Date == "2018-09-30", as_date("2018-10-01"), as_date(Date)),
         Date = as_date(Date), 
         Date = ifelse(grepl("O_015_687_Sma|O_015_920_Num", site_id) & Date == "2020-06-30", as_date("2020-07-01"), as_date(Date)), 
         Date = as_date(Date), 
         Date = ifelse(site_id == "F_234_229_Mas" & Date == "2018-10-30", as_date("2018-11-01"), as_date(Date)),
         Date = as_date(Date),
         Date = ymd(Date), year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'18/'20")) %>% 
  filter(year %in% c("2018", "2020")) %>% 
  distinct() %>% drop_na(TotP_ug_L) %>% 
  dplyr::select(c(site_id, year, month, okoregion, TotP_ug_L,  soil_moisture)) %>% 
  pivot_wider(names_from = year, values_from = TotP_ug_L) %>% 
  group_by(site_id, month) %>% 
  mutate(TP = log10(`2018`/`2020`)) %>% 
  dplyr::select(c(site_id, month,okoregion,TP,  soil_moisture))
           
TN_Ratio <- Water_Chem2 %>% 
  mutate(Date = ifelse(grepl("F_238_48_San|O_002_2053_Sto", site_id) & Date == "2018-09-30", as_date("2018-10-01"), as_date(Date)),
         Date = as_date(Date), 
         Date = ifelse(grepl("O_015_687_Sma|O_015_920_Num", site_id) & Date == "2020-06-30", as_date("2020-07-01"), as_date(Date)), 
         Date = as_date(Date), 
         Date = ifelse(site_id == "F_234_229_Mas" & Date == "2018-10-30", as_date("2018-11-01"), as_date(Date)),
         Date = as_date(Date),
         Date = ymd(Date), year = year(Date), month = month(Date, label = TRUE)) %>%  
  filter(group %in% c("'18/'20")) %>% 
  filter(year %in% c("2018", "2020")) %>% 
  distinct() %>% drop_na(TotN_ug_L) %>% 
  dplyr::select(c(site_id, year, month, okoregion, TotN_ug_L,  soil_moisture)) %>% 
  pivot_wider(names_from = year, values_from = TotN_ug_L) %>% 
  group_by(site_id, month) %>% 
  mutate(TN = log10(`2018`/`2020`)) %>% 
  dplyr::select(site_id, month, okoregion, TN,  soil_moisture)

# Nitrate
NO3_Ratio <- Water_Chem2 %>% 
 mutate(Date = ifelse(grepl("F_238_48_San|O_002_2053_Sto", site_id) & Date == "2018-09-30", as_date("2018-10-01"), as_date(Date)),
         Date = as_date(Date), 
         Date = ifelse(grepl("O_015_687_Sma|O_015_920_Num", site_id) & Date == "2020-06-30", as_date("2020-07-01"), as_date(Date)), 
         Date = as_date(Date), 
         Date = ifelse(site_id == "F_234_229_Mas" & Date == "2018-10-30", as_date("2018-11-01"), as_date(Date)),
         Date = as_date(Date),
         Date = ymd(Date), year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'18/'20")) %>% 
  filter(year %in% c("2018", "2020")) %>% 
  distinct() %>% drop_na(NO3_ug_L) %>% 
  dplyr::select(c(site_id, year, month, okoregion, NO3_ug_L,  soil_moisture)) %>% 
  pivot_wider(names_from = year, values_from = NO3_ug_L) %>% 
  group_by(site_id, month) %>% 
  mutate(NO3 = log10(`2018`/`2020`)) %>% 
  dplyr::select(site_id, month,okoregion, NO3,  soil_moisture)

NP_RatioP <- Water_Chem2 %>% 
 mutate(Date = ifelse(grepl("F_238_48_San|O_002_2053_Sto", site_id) & Date == "2018-09-30", as_date("2018-10-01"), as_date(Date)),
         Date = as_date(Date), 
         Date = ifelse(grepl("O_015_687_Sma|O_015_920_Num", site_id) & Date == "2020-06-30", as_date("2020-07-01"), as_date(Date)), 
         Date = as_date(Date), 
         Date = ifelse(site_id == "F_234_229_Mas" & Date == "2018-10-30", as_date("2018-11-01"), as_date(Date)),
         Date = as_date(Date),
         Date = ymd(Date), year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'18/'20")) %>% 
  filter(year %in% c("2018", "2020")) %>% 
  distinct() %>% drop_na(NO3_ug_L) %>% 
  dplyr::select(c(site_id, year, month, okoregion, NO3_ug_L, TotP_ug_L, soil_moisture)) %>% 
  group_by(site_id, year, month, okoregion) %>% 
  mutate(NP_Ratio = NO3_ug_L/TotP_ug_L) %>% 
  ungroup() %>% 
  dplyr::select(-c(NO3_ug_L, TotP_ug_L)) %>% 
  pivot_wider(names_from = year, values_from = NP_Ratio) %>% 
  group_by(site_id, month) %>% 
  mutate(NP_Ratio = log10(`2018`/`2020`)) %>% ungroup %>% 
  dplyr::select(c(site_id, month,okoregion, NP_Ratio,  soil_moisture))
           
X <- full_join(TP_Ratio, TN_Ratio)
XX <- full_join(NP_RatioP, NO3_Ratio) 

data <- full_join(X, XX) %>% 
  pivot_longer(cols= c(TP, TN, NO3,NP_Ratio), names_to = "variable", values_to = "logratio_18_20") %>% 
  drop_na() 

data$variable <- factor(data$variable, 
                       levels = c("NO3", "TN", "TP", "NP_Ratio"),
                       labels = c(bquote('NO'[3]),
                                  bquote("TotN"), 
                                  bquote("TotP"), 
                                  bquote('NO'[3]~':TotP')))

# T-tests
library(broom)
library(caret)
library(glue)

my.t.test.p.value <- function(...) {
    obj<-try(t.test(...), silent=TRUE)
    if (is(obj, "try-error")) return(NA) else return(obj$p.value)
 }

T_testR <- data %>%
  dplyr::select(site_id, okoregion, month, variable, logratio_18_20) %>% 
  ungroup() %>% distinct() %>% dplyr::select(-site_id) %>% 
  unite("ID", okoregion, month, variable, sep = "-", remove = TRUE) %>% 
  nest(data = -c(ID)) %>%  
  mutate(t_test = map(data, ~my.t.test.p.value(.x$logratio_18_20))) %>% 
  dplyr::select(-c(data)) %>% 
  unnest(t_test) %>% 
  mutate(p_value = round(t_test, 4)) %>% 
  dplyr::select(c(ID, p_value)) %>% 
  filter(p_value < 0.05) %>% 
  mutate(sign = "*") %>% 
  separate(ID, c("okoregion", "month", "variable"), sep = "-")


# Plot
library(scales)
Plot <- ggplot() +
  geom_point(data = data, aes(y = logratio_18_20, x = month, color = soil_moisture/100)) +
  geom_hline(yintercept=0, linetype="dashed", color = "black", size=0.5) +
  facet_grid(okoregion~variable,labeller = label_parsed) +
  scale_colour_gradient2(low = "red", mid = "red", high = "white", labels = percent) +
  theme_bw() +
  ylab(bquote('log'[10]~"(2018:2020)")) + xlab(NULL) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
  geom_text(data = T_testR, aes(y = 1.5, x = month, label = sign), size = 6, color = "black") +
  labs(color = "soil moisture")

ggsave("Figures/logratio_18_20.pdf", Plot, width = 9.5, height = 5, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/logratio_18_20.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/logratio_18_20.jpeg")
```

## Browning
```{r}
# Fe_ug_L, DOC_mg_L, Water_Color_mgPt_l

# Doubles need to be removed before ratios between 2018 and 2020 can be calculated
# F_238_48_San & O_002_2053_Sto #set/oct  change 2018-09-30 to 2018-10-01
# O_015_687_Sma & O_015_920_Num #jun/july change 2020-06-30 to 2020-07-01
# F_234_229_Mas #oct/nov change 2018-10-30 to 2018-11-01

# TP
DOC_Ratio <- Water_Chem2 %>% 
    mutate(Date = ifelse(grepl("F_238_48_San|O_002_2053_Sto", site_id) & Date == "2018-09-30", as.Date("2018-10-01"), as.Date(Date))) %>%
  mutate(Date = as.Date(Date)) %>%
  mutate(Date = ifelse(grepl("O_015_687_Sma|O_015_920_Num", site_id) & Date == "2020-06-30", as.Date("2020-07-01"), as.Date(Date))) %>%
   mutate(Date = as.Date(Date)) %>% 
  mutate(Date = ifelse(site_id == "F_234_229_Mas" & Date == "2018-10-30", as.Date("2018-11-01"), as.Date(Date))) %>%
  mutate(Date = as.Date(Date)) %>% 
  mutate(Date = ymd(Date), year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'18/'20")) %>% 
  filter(year %in% c("2018", "2020")) %>% 
  distinct() %>% drop_na(DOC_mg_L) %>% 
  dplyr::select(c(site_id, year, month, okoregion, DOC_mg_L,  soil_moisture)) %>% 
  pivot_wider(names_from = year, values_from = DOC_mg_L) %>% 
  group_by(site_id, month) %>% 
  mutate(DOC = log10(`2018`/`2020`)) %>% 
  dplyr::select(c(site_id, month,okoregion,DOC, soil_moisture))
           
Color_Ratio <- Water_Chem2 %>% 
    mutate(Date = ifelse(grepl("F_238_48_San|O_002_2053_Sto", site_id) & Date == "2018-09-30", as.Date("2018-10-01"), as.Date(Date))) %>%
  mutate(Date = as.Date(Date)) %>%
  mutate(Date = ifelse(grepl("O_015_687_Sma|O_015_920_Num", site_id) & Date == "2020-06-30", as.Date("2020-07-01"), as.Date(Date))) %>%
   mutate(Date = as.Date(Date)) %>% 
  mutate(Date = ifelse(site_id == "F_234_229_Mas" & Date == "2018-10-30", as.Date("2018-11-01"), as.Date(Date))) %>%
  mutate(Date = as.Date(Date)) %>% 
  mutate(Date = ymd(Date), year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'18/'20")) %>% 
  filter(year %in% c("2018", "2020")) %>% 
  distinct() %>% drop_na(Water_Color_mgPt_l) %>% 
  dplyr::select(c(site_id, year, month, okoregion, Water_Color_mgPt_l, soil_moisture)) %>% 
  pivot_wider(names_from = year, values_from = Water_Color_mgPt_l) %>% 
  group_by(site_id, month) %>% 
  mutate(Color = log10(`2018`/`2020`)) %>% 
  dplyr::select(site_id, month, okoregion, Color, soil_moisture)

Fe_Ratio <- Water_Chem2 %>% 
  mutate(Date = ifelse(grepl("F_238_48_San|O_002_2053_Sto", site_id) & Date == "2018-09-30", as.Date("2018-10-01"), as.Date(Date))) %>%
  mutate(Date = as.Date(Date)) %>%
  mutate(Date = ifelse(grepl("O_015_687_Sma|O_015_920_Num", site_id) & Date == "2020-06-30", as.Date("2020-07-01"), as.Date(Date))) %>%
   mutate(Date = as.Date(Date)) %>% 
  mutate(Date = ifelse(site_id == "F_234_229_Mas" & Date == "2018-10-30", as.Date("2018-11-01"), as.Date(Date))) %>%
  mutate(Date = as.Date(Date)) %>% 
  mutate(Date = ymd(Date), year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'18/'20")) %>% 
  filter(year %in% c("2018", "2020")) %>% 
  distinct() %>% drop_na(Fe_ug_L) %>% 
  dplyr::select(c(site_id, year, month, okoregion, Fe_ug_L, soil_moisture)) %>% 
  pivot_wider(names_from = year, values_from = Fe_ug_L) %>% 
  group_by(site_id, month) %>% 
  mutate(Fe = log10(`2018`/`2020`)) %>% 
  dplyr::select(site_id, month,okoregion, Fe, soil_moisture)
           
X <- full_join(DOC_Ratio, Color_Ratio)
data <- full_join(X, Fe_Ratio) %>% 
  pivot_longer(cols= c(DOC, Color, Fe), names_to = "variable", values_to = "logratio_18_20") %>% 
  drop_na() 


# T-tests
library(broom)
library(caret)
library(glue)

my.t.test.p.value <- function(...) {
    obj<-try(t.test(...), silent=TRUE)
    if (is(obj, "try-error")) return(NA) else return(obj$p.value)
 }

T_testR <- data %>%
  dplyr::select(site_id, okoregion, month, variable, logratio_18_20) %>% 
  ungroup() %>% distinct() %>% dplyr::select(-site_id) %>% 
  unite("ID", okoregion, month, variable, sep = "-", remove = TRUE) %>% 
  nest(data = -c(ID)) %>%  
  mutate(t_test = map(data, ~my.t.test.p.value(.x$logratio_18_20))) %>% 
  dplyr::select(-c(data)) %>% 
  unnest(t_test) %>% 
  mutate(p_value = round(t_test, 4)) %>% 
  dplyr::select(c(ID, p_value)) %>% 
  filter(p_value < 0.05) %>% 
  mutate(sign = "*") %>% 
  separate(ID, c("okoregion", "month", "variable"), sep = "-")

# Plot
library(scales)
Plot2 <- ggplot() +
  geom_point(data = data, aes(y = logratio_18_20, x = month, color = soil_moisture/100)) +
  geom_hline(yintercept=0, linetype="dashed", color = "black", size=0.5) +
  facet_grid(okoregion~variable,labeller = label_parsed) +
  scale_colour_gradient2(low = "red", mid = "red", high = "white", labels = percent) +
  theme_bw() +
  ylab(bquote('log'[10]~"(2018:2020)")) + xlab(NULL) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
  geom_text(data = T_testR, aes(y = 0.7, x = month, label = sign), size = 6, color = "black") +
  labs(color = "soil moisture")

ggsave("Figures/logratio_18_20_brown.pdf", Plot2, width = 9.5, height = 5, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/logratio_18_20_brown.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/logratio_18_20_brown.jpeg")
```


## Acidification
```{r}
# Temp_C, Ca_mg_L, pH, ANC_µEkv_L, 

# TP
Temp_Ratio <- Water_Chem2 %>% 
    mutate(Date = ifelse(grepl("F_238_48_San|O_002_2053_Sto", site_id) & Date == "2018-09-30", as.Date("2018-10-01"), as.Date(Date))) %>%
  mutate(Date = as.Date(Date)) %>%
  mutate(Date = ifelse(grepl("O_015_687_Sma|O_015_920_Num", site_id) & Date == "2020-06-30", as.Date("2020-07-01"), as.Date(Date))) %>%
   mutate(Date = as.Date(Date)) %>% 
  mutate(Date = ifelse(site_id == "F_234_229_Mas" & Date == "2018-10-30", as.Date("2018-11-01"), as.Date(Date))) %>%
  mutate(Date = as.Date(Date)) %>% 
  mutate(Date = ymd(Date), year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'18/'20")) %>% 
  filter(year %in% c("2018", "2020")) %>% 
  distinct() %>% drop_na(Temp_C) %>% 
  dplyr::select(c(site_id, year, month, okoregion, Temp_C, soil_moisture)) %>% 
  pivot_wider(names_from = year, values_from = Temp_C) %>% 
  group_by(site_id, month) %>% 
  mutate(Temp = log(`2018`/`2020`)) %>% 
  dplyr::select(c(site_id, month,okoregion,Temp, soil_moisture))
           
Ca_Ratio <- Water_Chem2 %>% 
    mutate(Date = ifelse(grepl("F_238_48_San|O_002_2053_Sto", site_id) & Date == "2018-09-30", as.Date("2018-10-01"), as.Date(Date))) %>%
  mutate(Date = as.Date(Date)) %>%
  mutate(Date = ifelse(grepl("O_015_687_Sma|O_015_920_Num", site_id) & Date == "2020-06-30", as.Date("2020-07-01"), as.Date(Date))) %>%
   mutate(Date = as.Date(Date)) %>% 
  mutate(Date = ifelse(site_id == "F_234_229_Mas" & Date == "2018-10-30", as.Date("2018-11-01"), as.Date(Date))) %>%
  mutate(Date = as.Date(Date)) %>% 
  mutate(Date = ymd(Date), year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'18/'20")) %>% 
  filter(year %in% c("2018", "2020")) %>% 
  distinct() %>% drop_na(Ca_mg_L) %>% 
  dplyr::select(c(site_id, year, month, okoregion, Ca_mg_L, soil_moisture)) %>% 
  pivot_wider(names_from = year, values_from = Ca_mg_L) %>% 
  group_by(site_id, month) %>% 
  mutate(Ca = log(`2018`/`2020`)) %>% 
  dplyr::select(site_id, month, okoregion, Ca, soil_moisture)

# ANC
ANC_Ratio <- Water_Chem2 %>% 
    mutate(Date = ifelse(grepl("F_238_48_San|O_002_2053_Sto", site_id) & Date == "2018-09-30", as.Date("2018-10-01"), as.Date(Date))) %>%
  mutate(Date = as.Date(Date)) %>%
  mutate(Date = ifelse(grepl("O_015_687_Sma|O_015_920_Num", site_id) & Date == "2020-06-30", as.Date("2020-07-01"), as.Date(Date))) %>%
   mutate(Date = as.Date(Date)) %>% 
  mutate(Date = ifelse(site_id == "F_234_229_Mas" & Date == "2018-10-30", as.Date("2018-11-01"), as.Date(Date))) %>%
  mutate(Date = as.Date(Date)) %>% 
  mutate(Date = ymd(Date), year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'18/'20")) %>% 
  filter(year %in% c("2018", "2020")) %>% 
  distinct() %>% drop_na(ANC_µEkv_L) %>% 
  dplyr::select(c(site_id, year, month, okoregion, ANC_µEkv_L, soil_moisture)) %>% 
  pivot_wider(names_from = year, values_from = ANC_µEkv_L) %>% 
  group_by(site_id, month) %>% 
  mutate(ANC = log(`2018`/`2020`)) %>% 
  dplyr::select(site_id, month,okoregion, ANC, soil_moisture)
           
X <- full_join(Temp_Ratio, Ca_Ratio)
data <- full_join(X, ANC_Ratio) %>% 
  pivot_longer(cols= c(Temp, Ca, ANC), names_to = "variable", values_to = "logratio_18_20") %>% 
  drop_na() 

# T-tests
library(broom)
library(caret)
library(glue)
library(scales)

my.t.test.p.value <- function(...) {
    obj<-try(t.test(...), silent=TRUE)
    if (is(obj, "try-error")) return(NA) else return(obj$p.value)
 }

T_testR <- data %>%
  dplyr::select(site_id, okoregion, month, variable, logratio_18_20) %>% 
  ungroup() %>% distinct() %>% dplyr::select(-site_id) %>% 
  unite("ID", okoregion, month, variable, sep = "-", remove = TRUE) %>% 
  nest(data = -c(ID)) %>%  
  mutate(t_test = map(data, ~my.t.test.p.value(.x$logratio_18_20))) %>% 
  dplyr::select(-c(data)) %>% 
  unnest(t_test) %>% 
  mutate(p_value = round(t_test, 4)) %>% 
  dplyr::select(c(ID, p_value)) %>% 
  filter(p_value < 0.05) %>% 
  mutate(sign = "*") %>% 
  separate(ID, c("okoregion", "month", "variable"), sep = "-")

# Plot
Plot3 <- ggplot() +
  geom_point(data = data, aes(y = logratio_18_20, x = month, color = soil_moisture/100)) +
  geom_hline(yintercept=0, linetype="dashed", color = "black", size=0.5) +
  facet_grid(okoregion~variable,labeller = label_parsed) +
  scale_colour_gradient2(low = "red", mid = "red", high = "white", labels = percent) +
  theme_bw() +
  ylab(bquote('log'[10]~"(2018:2020)")) + xlab(NULL) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
  geom_text(data = T_testR, aes(y = 1.5, x = month, label = sign), size = 6, color = "black") +
  labs(color = "soil moisture")

ggsave("Figures/logratio_18_20_Acid.pdf", Plot3, width = 9.5, height = 5, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/logratio_18_20_Acid.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/logratio_18_20_Acid.jpeg")
```


# Log ratios 2019/2021

# Nutrients
```{r}
Water_Chem_select <- read_csv("Clean_Data/Water_Chem_select.csv") 

# Doubles need to be removed before ratios between 

M_139_50_Lur
M_139_219_San
N_195_59_Fla
S_021_1187_Ves

# TP
TP_Ratio <- Water_Chem_select %>% 
  mutate(Date = as.Date(Date)) %>% 
  mutate(Date = ymd(Date), year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'19/'21")) %>% 
  filter(year %in% c("2019", "2021")) %>% 
  distinct() %>% drop_na(TotP_ug_L) %>% 
  dplyr::select(c(site_id, year, month, okoregion, TotP_ug_L)) %>% 
  ungroup() %>% distinct() %>% 
      dplyr::group_by(site_id, month, okoregion, year) %>%
    dplyr::summarise(n = dplyr::n(), .groups = "drop") %>%
    dplyr::filter(n > 1L)
  pivot_wider(names_from = year, values_from = TotP_ug_L) %>% 
  group_by(site_id, month) %>% 
  mutate(TP = log(`2019`/`2021`)) %>% 
  dplyr::select(c(site_id, month,okoregion,TP))
           
TN_Ratio <- Water_Chem_select %>% 
  mutate(Date = as.Date(Date)) %>% 
  mutate(Date = ymd(Date), year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'19/'21")) %>% 
  filter(year %in% c("2019", "2021")) %>% 
  distinct() %>% drop_na(TotN_ug_L) %>% 
  dplyr::select(c(site_id, year, month, okoregion, TotN_ug_L)) %>% 
  pivot_wider(names_from = year, values_from = TotN_ug_L) %>% 
  group_by(site_id, month) %>% 
  mutate(TN = log(`2019`/`2021`)) %>% 
  dplyr::select(site_id, month, okoregion, TN)

# Nitrate
NO3_Ratio <- Water_Chem_select %>% 
  mutate(Date = as.Date(Date)) %>% 
  mutate(Date = ymd(Date), year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'19/'21")) %>% 
  filter(year %in% c("2019", "2021")) %>% 
  distinct() %>% drop_na(NO3_ug_L) %>% 
  dplyr::select(c(site_id, year, month, okoregion, NO3_ug_L)) %>% 
  pivot_wider(names_from = year, values_from = NO3_ug_L) %>% 
  group_by(site_id, month) %>% 
  mutate(NO3 = log(`2019`/`2021`)) %>% 
  dplyr::select(site_id, month,okoregion, NO3)
           
X <- full_join(TP_Ratio, TN_Ratio)
XX <- full_join(X, NO3_Ratio) %>% 
  pivot_longer(cols= c(TP, TN, NO3), names_to = "variable", values_to = "logratio_19_21") %>% 
  drop_na() 

Plot <- XX %>% 
  ggplot(aes(y = logratio_19_21, x = month, color = month)) +
  geom_point() +
  ylab("log10([2019]:[2021]") + xlab(NULL) +
  geom_hline(yintercept=0, linetype="dashed", color = "black", size=0.5) +
  facet_grid(okoregion~variable) +
  theme_bw() + theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) 

ggsave("Figures/logratio_19_21.pdf", Plot, width = 7.5, height = 5, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/logratio_19_21.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/logratio_19_21.jpeg")
```


## Browning
```{r}
# Fe_ug_L, DOC_mg_L, Water_Color_mgPt_l

Water_Chem_select <- read_csv("Clean_Data/Water_Chem_select.csv") 

# Doubles need to be removed before ratios between 2018 and 2020 can be calculated
# F_238_48_San & O_002_2053_Sto #set/oct  change 2018-09-30 to 2018-10-01
# O_015_687_Sma & O_015_920_Num #jun/july change 2020-06-30 to 2020-07-01
# F_234_229_Mas #oct/nov change 2018-10-30 to 2018-11-01
names(Water_Chem_select)
# TP
DOC_Ratio <- Water_Chem_select %>% 
  mutate(Date = as.Date(Date)) %>% 
  mutate(Date = ymd(Date), year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'19/'21")) %>% 
  filter(year %in% c("2019", "2021")) %>% 
  distinct() %>% drop_na(DOC_mg_L) %>% 
  dplyr::select(c(site_id, year, month, okoregion, DOC_mg_L)) %>% 
    dplyr::group_by(site_id, month, okoregion, year) %>%
    dplyr::summarise(n = dplyr::n(), .groups = "drop") %>%
    dplyr::filter(n > 1L)
  pivot_wider(names_from = year, values_from = DOC_mg_L) %>% 
  group_by(site_id, month) %>% 
  mutate(DOC = log(`2019`/`2021`)) %>% 
  dplyr::select(c(site_id, month,okoregion,DOC))
           
Color_Ratio <- Water_Chem_select %>% 
  mutate(Date = as.Date(Date)) %>% 
  mutate(Date = ymd(Date), year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'19/'21")) %>% 
  filter(year %in% c("2019", "2021")) %>% 
  distinct() %>% drop_na(Water_Color_mgPt_l) %>% 
  dplyr::select(c(site_id, year, month, okoregion, Water_Color_mgPt_l)) %>% 
  pivot_wider(names_from = year, values_from = Water_Color_mgPt_l) %>% 
  group_by(site_id, month) %>% 
  mutate(Color = log(`2019`/`2021`)) %>% 
  dplyr::select(site_id, month, okoregion, Color)

# Nitrate
Fe_Ratio <- Water_Chem_select %>% 
  mutate(Date = as.Date(Date)) %>% 
  mutate(Date = ymd(Date), year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'19/'21")) %>% 
  filter(year %in% c("2019", "2021")) %>% 
  distinct() %>% drop_na(Fe_ug_L) %>% 
  dplyr::select(c(site_id, year, month, okoregion, Fe_ug_L)) %>% 
  pivot_wider(names_from = year, values_from = Fe_ug_L) %>% 
  group_by(site_id, month) %>% 
  mutate(Fe = log(`2019`/`2021`)) %>% 
  dplyr::select(site_id, month,okoregion, Fe)
           
X <- full_join(DOC_Ratio, Color_Ratio)
XX <- full_join(X, Fe_Ratio) %>% 
  pivot_longer(cols= c(DOC, Color, Fe), names_to = "variable", values_to = "logratio_19_21") %>% 
  drop_na() 

Plot2 <- XX %>% 
  ggplot(aes(y = logratio_19_21, x = month, color = month)) +
  geom_point() +
  ylab("log([2019]:[2021]") + xlab(NULL) +
  geom_hline(yintercept=0, linetype="dashed", color = "black", size=0.5) +
  facet_grid(okoregion~variable) +
  theme_bw() + theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) 

ggsave("Figures/logratio_19_21_brown.pdf", Plot2, width = 6.5, height = 5, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/logratio_19_21_brown.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/logratio_19_21_brown.jpeg")
```


## Acidification
```{r}
# Temp_C, Ca_mg_L, pH, ANC_µEkv_L, 
Water_Chem_select <- read_csv("Clean_Data/Water_Chem_select.csv") 

# Doubles need to be removed before ratios between 
names(Water_Chem_select)
# TP
Temp_Ratio <- Water_Chem_select %>% 
  mutate(Date = as.Date(Date)) %>% 
  mutate(Date = ymd(Date), year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'19/'21")) %>% 
  filter(year %in% c("2019", "2021")) %>% 
  distinct() %>% drop_na(Temp_C) %>% 
  dplyr::select(c(site_id, year, month, okoregion, Temp_C)) %>% 
  pivot_wider(names_from = year, values_from = Temp_C) %>% 
  group_by(site_id, month) %>% 
  mutate(Temp = log(`2019`/`2021`)) %>% 
  dplyr::select(c(site_id, month,okoregion,Temp))
           
Ca_Ratio <- Water_Chem_select %>% 
  mutate(Date = as.Date(Date)) %>% 
  mutate(Date = ymd(Date), year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'19/'21")) %>% 
  filter(year %in% c("2019", "2021")) %>% 
  distinct() %>% drop_na(Ca_mg_L) %>% 
  dplyr::select(c(site_id, year, month, okoregion, Ca_mg_L)) %>% 
  pivot_wider(names_from = year, values_from = Ca_mg_L) %>% 
  group_by(site_id, month) %>% 
  mutate(Ca = log(`2019`/`2021`)) %>% 
  dplyr::select(site_id, month, okoregion, Ca)

# ANC
ANC_Ratio <- Water_Chem_select %>% 
  mutate(Date = as.Date(Date)) %>% 
  mutate(Date = ymd(Date), year = year(Date), month = month(Date, label = TRUE)) %>% 
  filter(group %in% c("'19/'21")) %>% 
  filter(year %in% c("2019", "2021")) %>% 
  distinct() %>% drop_na(ANC_µEkv_L) %>% 
  dplyr::select(c(site_id, year, month, okoregion, ANC_µEkv_L)) %>% 
  pivot_wider(names_from = year, values_from = ANC_µEkv_L) %>% 
  group_by(site_id, month) %>% 
  mutate(ANC = log(`2019`/`2021`)) %>% 
  dplyr::select(site_id, month,okoregion, ANC)
           
X <- full_join(Temp_Ratio, Ca_Ratio)
XX <- full_join(X, ANC_Ratio) %>% 
  pivot_longer(cols= c(Temp, Ca, ANC), names_to = "variable", values_to = "logratio_19_21") %>% 
  drop_na() 

Plot3 <- XX %>% 
  ggplot(aes(y = logratio_19_21, x = month, color = month)) +
  geom_point() +
  ylab("log([2019]:[2021]") + xlab(NULL) +
  geom_hline(yintercept=0, linetype="dashed", color = "black", size=0.5) +
  facet_grid(okoregion~variable) +
  theme_bw() + theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) 

ggsave("Figures/logratio_19_21_Acid.pdf", Plot3, width = 6.5, height = 5, bg = "white", device = cairo_pdf)
bitmap <- pdf_render_page("Figures/logratio_19_21_Acid.pdf", page = 1, dpi = 300)
jpeg::writeJPEG(bitmap, "Figures/logratio_19_21_Acid.jpeg")
```


